### 2019-06-01 README.Rmd
Initial commit

---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
# Please put your title here to include it in the file below. 
Title <- "Title of your paper goes here"
```

# replicationteachingarchaeology

This repository contains the data and code for our paper:

> Authors, (YYYY). _`r Title`_. Name of journal/book <https://doi.org/xxx/xxx>

Our pre-print is online here:

> Authors, (YYYY). _`r Title`_. Name of journal/book, Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/xxx/xxx>

### How to cite

Please cite this compendium as:

> Authors, (`r format(Sys.Date(), "%Y")`). _Compendium of R code and data for `r Title`_. Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/xxx/xxx>

### How to download or install

You can download the compendium as a zip from from this URL: </archive/master.zip>

Or you can install this compendium as an R package, replicationteachingarchaeology, from GitHub with:
### Licenses

**Text and figures :**  [CC-BY-4.0](http://creativecommons.org/licenses/by/4.0/)

**Code :** See the [DESCRIPTION](DESCRIPTION) file

**Data :** [CC-0](http://creativecommons.org/publicdomain/zero/1.0/) attribution requested in reuse

### Contributions

We welcome contributions from everyone. Before you get started, please see our [contributor guidelines](CONTRIBUTING.md). Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md). By participating in this project you agree to abide by its terms.

### 2019-06-01 analysis/paper/paper.Rmd
initial

---
title: "How to use replication assignments for teaching integrity in empirical archaeology"
author:
  - Ben Marwick, bmarwick@uw.edu
  - Liying Wang
  - Ryan Robinson
  - Hope Loiselle
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
    bookdown::html_document2:
      fig_caption: yes
      reference_docx: "../templates/template.docx" # Insert path for the DOCX file
bibliography: references.bib
csl: "../templates/journal-of-archaeological-science.csl" # Insert path for the bib-style
abstract: |
  Text of abstract
keywords: |
  keyword 1; keyword 2; keyword 3
highlights: |
  These are the highlights. 
---

```{r, setup, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  echo = FALSE,
  comment = "#>",
  fig.path = "../figures/"
)
```

```{r setup2, eval = FALSE}
# devtools::install_github("ekothe/rmdrive")
library(rmdrive)

# get text from google doc into Rmd
download_rmd(file = "paper",  # do not include the .Rmd 
             gfile = "Paper: Replication projects for teaching integrity in empirical archaeology")  # name of google doc file

# push updates from Rmd to google doc
update_rmd(file = "analysis/paper/paper",    # do not include the .Rmd 
           gfile = "Paper: Replication projects for teaching integrity in empirical archaeology")  # name of google doc file

```

## Introduction

In many research communities there are changes underway that promote or require high levels of transparency and reproducibility of research. For example... using open source programming language such as R or Python...

Archaeologists are increasingly adopting these practices also. For example… However current norms in teaching archaeology are out of step with these practices. Given shifts in community values, it is important that we prepare our students with the skills necessary to fulfill these expectations of greater transparency and reproducibility in research. Here we propose a new type of assignment, the replication report, to better align the practice of teaching archaeology with the ideals of archaeological practise. The replication report assignment involves students analysing a published report to determine the main claims made by the authors of that report, students obtaining the data used by the authors, and analysing that data to determine if one or more of the authors’ claims are reliable.

In this paper we describe how to implement a replication report assignment suitable for upper level undergraduates and graduate students in archaeology. Our experience is based on an upper level archaeology class on stone artefact analysis taught at the University of Washington. The class format includes a weekly cycle of lecture, discussion seminar, and hands-on laboratory activities. The assignments include seminar notes, lecture quizzes, laboratory worksheets, and two longer empirical reports. For the term that we report here, the class had 16 students, a typical number for this class, and similar to the usual size of upper-level laboratory classes in the archaeology program at the University of Washington. Here we survey the literature on similar types of assignments in other fields to identify common elements that other fields have identified as important principles and skills. We describe our assignment and discuss student feedback on the our implementation. Finally we offer recommendations for how to use replication reports to teach archaeology students.

## Background

Definitions of ‘replication’ vary across difference research areas and sometimes confused with ‘reproducibility’. Some examples in different fields… Definitions of reproducibility vs replicability are contested, survey a few and then declare we will use the ones from here: http://sites.nationalacademies.org/sites/reproducibility-in-science/index.htm

What other fields already do this…
What journals require replication materials? And what exactly do they require?
What previous examples of replication assignments in other fields? What do they have in common? What are the typical and unusual elements?

LY- economics: Ball, R., & Medeiros, N. (2012). Teaching integrity in empirical research: A protocol for documenting data management and analysis. The Journal of Economic Education, 43(2), 182-189.   https://www.tandfonline.com/doi/abs/10.1080/00220485.2012.659647 https://www.bitss.org/wp-content/uploads/2014/06/teaching-integrity-in-empirical-research-required1.pdf

HL- international studies: Janz, N. (2016). Bringing the gold standard into the classroom: replication in university teaching. International Studies Perspectives, 17(4), 392-407. https://doi.org/10.1111/insp.12104

RR - computer networking: Yan, L., & McKeown, N. (2017). Learning networking by reproducing research results. ACM SIGCOMM Computer Communication Review, 47(2), 19-26. https://ccronline.sigcomm.org/wp-content/uploads/2017/05/acmdl17-97.pdf

LY - neuroscience: Millman, K. J., Brett, M., Barnowski, R., & Poline, J. B. (2018). Teaching computational reproducibility for neuroimaging. Frontiers in neuroscience, 12, 727. https://www.frontiersin.org/articles/10.3389/fnins.2018.00727/full

## Methods

Our replication report assignment consisted of three small, graded activities to scaffold the preparation of the final report. Each step was separated by one week to give students time to work. Submissions for each step were graded as complete/incomplete, with feedback provided individually via the Canvas learning management system, and during class meetings.

For the first step we supplied students with a list of journal articles that included raw data and R code either in supplemental files or deposited on open data repositories. This list is updated regularly, but is not exhaustive and is currently online at https://github.com/benmarwick/ctv-archaeology Working in groups of 3-4 people, students selected a journal article from this list as their target article for this assignment. We encouraged them to choose a target article about a stone artefact analysis that looked interesting to them. We also required students to set up an open communication channel for their group to ensure they had an easy way to discuss their selection of the target article. We used Slack, a free cloud-based web application for team communication. The instructors were members of all the student group channels to give guidance and support good communication habits. Students were required to individually submit the full bibliographic reference for their target article to complete step one.

For step two of the assignment, students were required to discuss in their groups to identify 2-3 key claims made by the authors of their target article. They were told to study the data visualizations in the paper to identify which figures seem to give the best support to the authors' claims. Recreating these 1-2 key visualisations was a key task in the production of the final report. A second task for step two was for students to identify and obtain the raw data files of their target article. The list of articles that the students chose from only included articles for which data were openly available. This removed the need for students to contact authors to request data, which may have added the risk of a long wait, refusal to share, or no reply. To complete step two, each student was required to submit a short statement summarising the 2-3 key claims of their target paper, and the raw data file.

Step three of the assignment required students to create a file structure on their computer to organise their assignment files, to download an R Markdown file and write a small amount of R code to read in the raw data and explore it with one basic visualisation, unrelated to any in the target article. We prepared an R Markdown file with some basic headings (following the IMRaD or  Introduction-Method-Results-and-Discussion format) and empty code chunks to provide guidance on how many code chunks were expected, and where in the document they should appear. As students wrote their R code and encountered errors, they were encouraged to share screenshots on Slack for the instructors to assist with troubleshooting. After completing this step, the instructor met with each group to review the main claims identified by the students, review the visualisation they had chosen to replicate, and provide guidance on writing the R code to produce the key visualisations.

The final task was for the students to write their report, and submit a reproducible research compendium. This included three files: (1) their R Markdown document, (2)  the raw data file, and (3) the output document (e.g. Microsoft Word document that is produced when they knit the R Markdown file). Our expectation was that we could create any student’s results by running their submitted R Markdown document and the raw data file to produce the Word document they submitted. The final report was graded with a rubric which was presented to the students at the first step to help set expectations about what the final product should look like.

In the time between students submitting their final report and the grades being released we administered an  survey to obtain feedback anonymously from the students. The purpose of the feedback survey was to collect information about how to improve the assignment for future classes, to understand the students’ experience of the assignment, and what value they perceive in replication skills for archaeology in general, and for them individually.

## Results

### Observations on the assignment process

The first step, choosing the target article, revealed the need for some intervention from the instructor to guide students to articles that used relatively simple statistical methods. For example, one group initially chose @Breslawski_Etter_Jorgeson_Boulanger_2018 as their target article, but the key claims in this paper depend on multiple comparisons of multilevel regression models. We explained to the students that if they attempted to replicate a key claim of this paper then they would likely be doing substantially more work than other groups in the class. We invited this group to choose a different target article to ensure a more comparable experience, which they accepted. The statistical backgrounds of our students was highly diverse, so we could not expect students to be very discerning about the statistical complexity of the methods in the articles on the list of potential target articles. As a consequence, we were prepared to intervene to guide their selection of a paper that we could be sure they could successfully replicate, given the time available.

The second step was mostly straightforward, with students engaging in discussion in class and on Slack to identify the 2-3 key claims of their target paper, and identify the data visualisation that provided the most relevant support to one or more of those claims. Identifying the data files was less straightforward, with about one third of students failing to correctly identify the data files accompanying their target article. We attribute this to the relatively low level of familiarity of the students in working with raw data, so they are not sure when they are looking at it, and the high degree of variability in how the target article authors make their data open. Some authors include their data as a file in the supplementary information attached to the article, while others deposit their files on an open data repository such as osf.io or figshare.com, and then cite the DOI to the files in their article. Where the data files were nested in several layers of folders, some students struggled to find them.

The ability to easily share screenshots on Slack was important to the success of the third step. Our intention was that two lab classes earlier in the term that introduced students to some methods for data visualization using R would provide the foundation for succeeding in this step. However, we found that for some students this was not sufficient practice, and substantial instructor guidance was required to help them complete this step. At the completion of this step, the instructor met one on one with each group to check how successful they were producing a basic visualization using data from the target article, and to discuss the group's strategy to complete the report. This was the most time-consuming aspect of the assignment for the instructor, holding a one hour meeting with each of the five groups.

## Analysis of the students' anonymous feedback

Our course had no prerequisites, so we assumed no prior knowledge of R among the students, and were prepared to teach them as complete novices. We were also prepared for students to have no prior experience with replication report assignments. Other courses in our program at UW do not include this kind of assignment, and they are not common in other programs, to the best of our knowledge. We posted to the Society of American Archaeology Teaching Archaeology Interest Group to ask for examples of replication reports used in teaching archaeology, and received no replies.

```{r}
library(tidyverse)
feedback <- read_csv(here::here("analysis/data/raw_data/Replication report feedback Survey Student Analysis Report.csv"))

```

describe results of follow-up survey: https://canvas.uw.edu/courses/1272207/quizzes/1134059/statistics

Discussion and conclusion

Recommendations… future plans

Table and Figures:

Survey of replication report assignments in other fields
Instructions to students
Grading rubric
R Markdown template snippet 
Feedback survey facet plot

<!-- The following line inserts a page break when the output is MS Word. For page breaks in PDF, use \newpage on its own line.  -->
##### pagebreak

# References 
<!-- The following line ensures the references appear here for the MS Word or HTML output files, rather than right at the end of the document (this will not work for PDF files):  -->
<div id="refs"></div>

##### pagebreak

### Colophon

This report was generated on `r Sys.time()` using the following computational environment and dependencies:

```{r colophon, cache = FALSE}
# which R packages and versions?
devtools::session_info()
```

The current Git commit details are:

```{r}
# what commit is this file at? 
git2r::repository(here::here())
```

________________

Notes:

Target journal: Advances in Archaeological Practice - how to section 3500 words “clear, concise, step-by-step guidelines for successfully completing tasks that are or are becoming common practice”

Key papers to read and cite:

Ball, R., & Medeiros, N. (2012). Teaching integrity in empirical research: A protocol for documenting data management and analysis. The Journal of Economic Education, 43(2), 182-189. https://www.bitss.org/wp-content/uploads/2014/06/teaching-integrity-in-empirical-research-required1.pdf

Toelch, U., & Ostwald, D. (2018). Digital open science—Teaching digital tools for reproducible and transparent research. PLoS biology, 16(7), e2006022. https://journals.plos.org/plosbiology/article?id=10.1371/journal.pbio.2006022

Medeiros, N., & Ball, R. J. (2017). Teaching Integrity in Empirical Economics: The Pedagogy of Reproducible Science in Undergraduate Education. https://scholarship.haverford.edu/cgi/viewcontent.cgi?article=1189&context=economics_facpubs

Hicks, S. C., & Irizarry, R. A. (2018). A guide to teaching data science. The American Statistician, 72(4), 382-391.

Janz, N. (2016). Bringing the gold standard into the classroom: replication in university teaching. International Studies Perspectives, 17(4), 392-407. https://doi.org/10.1111/insp.12104

Jern, A. (2018). A preliminary study of the educational benefits of conducting replications in the classroom. Scholarship of Teaching and Learning in Psychology, 4(1), 64.

Çetinkaya-Rundel, M., & Rundel, C. (2018). Infrastructure and tools for teaching computing throughout the statistical curriculum. The American Statistician, 72(1), 58-65.

Yan, L., & McKeown, N. (2017). Learning networking by reproducing research results. ACM SIGCOMM Computer Communication Review, 47(2), 19-26. https://ccronline.sigcomm.org/wp-content/uploads/2017/05/acmdl17-97.pdf

Millman, K. J., Brett, M., Barnowski, R., & Poline, J. B. (2018). Teaching computational reproducibility for neuroimaging. Frontiers in neuroscience, 12, 727. https://www.frontiersin.org/articles/10.3389/fnins.2018.00727/full

Wessa, P. (2009). How Reproducible Research Leads to Non-Rote Learning within Socially Constructivist Statistics Education. Electronic Journal of e-Learning, 7(2), 173-182.

https://politicalsciencereplication.wordpress.com/2014/04/02/reproducibility-pioneers-political-scientists-assigning-replications-to-students/

https://www.washingtonpost.com/news/monkey-cage/wp/2014/02/12/replication-in-political-science-graduate-courses-an-untapped-resource/?noredirect=on&utm_term=.a557ce616b59

https://docs.google.com/forms/d/e/1FAIpQLSeRk7_4Rrzb3DafYGD4NYFjlNJ1rct50iPzzsEuxk6kiID-ag/viewform

Apply for Sloan foundation for a survey and study of data availability https://sloan.org/programs/digital-technology/scholarly-communication https://sloan.org/grants/apply#tab-letters-of-inquiry
________________

For each case study of a class that uses a replication assignment, we want to know

Variable
	Ball and Medeiros (2012)
	Ball (2018)
	Janz 2016
	Millman et al.(2018) 
	Yan & McKeown 2017
	etc
	How long (year/term/week)?
	A term

	8 weeks
	fall semester, 17 weeks 
	Three weeks

	How many students?
	NA

	~15

	200 students over 5 years

	Group or individual?
	individual

	individual
	group
	In pairs

	Main software tool (R/Python/??)?
	Stata

	R
	Python
	Amazon Web Services EC2

	Using Markdown/LaTeX/??
	NA
	R Markdown
	NA
	Markdown
	NA

	Using Git/GitHub or not?
	NA

	NA
	Git and GitHub
	NA

	Using CI (e.g. Travis) or not?
	NA

	NA
	Travis CI, Circle CI, and Appveyor
	No

	In class presentation or not?
	NA

	Yes
	Yes
	Yes

	Peer review by other students or not?
	NA

	Yes
	Yes
	Yes

	Students contact original study authors or not?
	NA

	Yes

	Yes

	Public posting of results by students (e.g. blog, osf.io, other repository) or not?
	Yes, Haverford College Library

	Yes

	Yes

________________

Notes on the background readings

Ball and Medeiros (2012)

To achieve the goal of fostering and teaching reproducible research, Ball and Medeiros (2012) developed a protocol for documenting statistical analyses for economics undergraduates to use for their empirical research projects. Instead of partial replication for final results, their 'soup to nut' approach suggests that the standards of replicability must contain four elements, including raw data files, associated metadata, all commands of data processing and analysis, and public availability. This approach establishes norms for complete documentation of empirical research to ensure researchers could successfully reproduce the results by reducing difficulties encountered during replication due to insufficient and partial sharing of data and analytical processes. Moreover, the transparency and reproducible of data bring important pedagogical benefits for students at all stages of completing their projects. Command files enable students to work with the data more efficient and have better data management by keeping track of each step they have done, and the most importantly, complete documentation of research helps students to take responsibility and accountability for their work.

Janz, Nicole. 2016. “Bringing the Gold Standard into the Classroom: Replication in University Teaching.” International Studies Perspectives 17: 392-407. 
·     Janz argues for bringing replication assignments into the graduate teaching program of political science
·     These assignments would do well in methods classes both to train in methods and to teach how to make work reproducible
·     In some courses for younger students, a duplication may be more beneficial, in upper level classes, a replication where original work is tested, plus new analyses or data can be added and potentially published
·     Replication studies allow a student to learn with original data, including bugs and flaws and to follow along the logic of the author
·     Teaches students how to make their own work reproducible in the future
·     Goes beyond literature review in helping students understand the field
·     This article addresses some criticisms as well: this does not promote error-hunting, and in fact, it was better for students when there were no errors, it does not hurt the reputation of other scientists, their work should be correct in the first place
·     Her class was interdisciplinary which she found very valuable for idea sharing, but difficult because people came in with different skill levels

Yan & McKeown (2017)
* The authors argue that replication assignments in graduate level courses provide more qualitative learning, inspire future research, and improve the networking community
* Networking graduate students at Stanford learn in a unique top-down manner that encourages them to learn the deeper mechanisms of the Internet
* Building from that approach, they were asked to create their own projects -- but these were lacking due to the time constraints of a term and overly ambitious projects
* Instead, students asked to replicate "classic" netowrking papers
* 200 students over 5 years (2012-2017), 40 unique papers reproduced & projects published on course blog
* Work emulated in Mininet or Mahimahi (or another emulator if the original authors did so)
* Students who fail to correctly replicate results are still considered successful if their results resemble the general shape of the original, or if they are able to reflect and identify their own mistakes
* The "large majority" finished their projects by correctly replicating the original results
* Peer review and peer replication: pairs will end the assignment by reproducing another pair's replication
* Primary reason for the project is unique educational and experiential value
* Recreating the experiment is time consuming but very fulfulling. Students learned the paper much better by immersing themselves in it
* Unexpectedly, this project contributes to networking community as students verify work or expose inconsistencies 
* Students acquire new professional skills that they otherwise would not have

### 2019-06-01 analysis/paper/paper.Rmd
likert plot

@@
 
-```{r}
+```{r feedback-data-prep}
 library(tidyverse)
@@
 
+# tidy the variable names
+feedback <- 
+  feedback %>% 
+  rename_all(list(~str_squish(str_remove(., "\\d*:"))))
+
+# extract yes/no questions
+feedback_yn <- 
+  feedback %>% 
+  select(6, 8)
+
+# extract likert-scale questions
+feedback_likert <- 
+  feedback %>% 
+  select(seq(10, 19, 2)) %>% 
+  mutate_all(as.factor)  %>% 
+  mutate_all(tolower) %>% 
+  as.data.frame()
+```
+
+```{r likert-plot}
+mylevels <- c('strongly disagree', 'disagree', 'neutral', 'agree', 'strongly agree')
+
+# Here we will recode each factor and explicitly set the levels
+for(i in seq_along(feedback_likert)) {
+	feedback_likert[,i] <- factor(feedback_likert[,i], levels=mylevels)
+}
+
+require(likert)
+feedback_likert_out <- likert(feedback_likert)
+plot(feedback_likert_out, wrap = 30)
 ```

### 2019-06-10 analysis/paper/plot-feedback-survey.R
output plots

@@ -1,0 +1,85 @@
+
+library(tidyverse)
+feedback <- read_csv(here::here("analysis/data/raw_data/Replication report feedback Survey Student Analysis Report.csv"))
+
+# --- tidy-the-variable-names ---
+feedback <-
+  feedback %>%
+  rename_all(list(~str_squish(str_remove(., "\\d*:"))))
+
+# --- extract-yes-no-questions ---
+feedback_yn <-
+  feedback %>%
+  select(6, 8)
+
+# --- extract-likert-scale-questions ---
+feedback_likert <-
+  feedback %>%
+  select(seq(10, 19, 2)) %>%
+  mutate_all(as.factor)  %>%
+  mutate_all(tolower) %>%
+  as.data.frame()
+
+mylevels <- c('strongly disagree', 'disagree', 'neutral', 'agree', 'strongly agree')
+
+# Here we will recode each factor and explicitly set the levels
+for(i in seq_along(feedback_likert)) {
+  feedback_likert[,i] <- factor(feedback_likert[,i], levels=mylevels)
+}
+
+# --- plot-likert ---
+require(likert)
+feedback_likert_out <- likert(feedback_likert)
+plot_l <- plot(feedback_likert_out,
+               wrap = 30,
+               legend.position = "top",
+               base_size = 10)
+
+# --- plot-y-n
+plot_y <-
+feedback_yn %>%
+  gather(variable, value) %>%
+  group_by(variable, value) %>%
+  tally() %>%
+  mutate(response = ifelse(str_detect(value, "No"), "No", "Yes")) %>%
+  mutate(question = str_wrap(variable, 30)) %>%
+  ggplot(aes(question,
+             n,
+             fill = response)) +
+  geom_col() +
+  labs(x = "",
+       y = "Number of responses") +
+  coord_flip() +
+  theme_minimal(base_size = 10) +
+  scale_fill_grey()
+
+# --- combine-plots
+library(cowplot)
+plot_grid(plot_l,
+          plot_y,
+          ncol =1,
+          rel_heights = c(4, 1))
+
+ggsave('analysis/figures/feedback_likert_yn_plot.png',
+                  height = 8,
+                  width = 12)
+
+
+# --- likert-cor
+library(corrr)
+feedback_likert_out$results %>%
+  gather(variable, value, -Item) %>%
+  mutate(Item = str_wrap(Item, 20)) %>%
+  spread(Item, value) %>%
[…]

### 2019-06-10 analysis/paper/plot-rubric-scores.R

@@ -1,0 +1,81 @@
+
+
+library(tidyverse)
+library(ggbeeswarm)
+
+#' read in the data
+# what a mess
+grading_rubric <- readxl::read_excel("analysis/data/raw_data/grading-rubric.xlsx")
+
+#' clean the data
+criteria <-
+  grading_rubric %>%
+  select(1) %>%
+  # get every second row
+  filter(row_number() %% 2 == 1) %>%
+  slice(1:12) %>%
+  pull()
+
+criteria_short <- c(
+"Content: submission includes Rmd file, Data file, and Word file"
+,"Content: maximum of 500 words"
+,"Content: minimum of 4 scholarly items in the reference list"
+,"Intro: has clear statement of the purpose of the report"
+,"Intro: has background to debate"
+,"Intro: has names, locations, and basic chronology of sites"
+,"Methods: identify the specific results you will replicate"
+,"Methods: describe the specific methods that you used to validate these results"
+,"Results: includes 1-2 original plots & description of these"
+, "Conclusion:state whether the author’s claims appear to be robust, unreliable, etc"
+, "Style: Use efficient and succinct sentences, no direct quotes"
+, "Style: Use commas and apostrophes correctly, and spell consistently"
+)
+
+# clean up the scores from canvas, one col per student
+clean_and_ratio_the_score <-
+  function(x) {
+    str_remove_all(x, "/|pts") %>%
+      str_squish() %>%
+      str_split(" ") %>%
+      unlist() %>%
+      parse_number() %>%
+      enframe() %>%
+      spread(name, value) %>%
+      mutate(prop = `1` / `2`) %>%
+      pull(prop) %>%
+      as.numeric()
+  }
+
+#
+scores <-
+grading_rubric %>%
+  select(contains("Ratings")) %>%
+  # get every second row
+  filter(row_number() %% 2 == 0) %>%
+  mutate(criteria = criteria_short) %>%
+  gather(student, score, -criteria) %>%
+  mutate(prop = map_dbl(score, clean_and_ratio_the_score))
+
+#' Plot the distribution of scores
+scores %>%
+  mutate(criteria = str_wrap((criteria), 40)) %>%
+  ggplot(aes(reorder(criteria, prop),
+             prop)) +
+  geom_quasirandom(alpha = 0.3,
+              size = 5) +
+  stat_summary(fun.y=mean,
+               geom="point",
+               shape="\U007C",
+               size=15,
+               colour="red") +
[…]

### 2019-06-10 analysis/paper/paper.Rmd
output plots
update from google docs

--- 2019-06-01 analysis/paper/paper.Rmd
@@
   - Liying Wang
-  - Ryan Robinson
-  - Hope Loiselle
 date: "`r format(Sys.time(), '%d %B, %Y')`"
@@
 ```{r setup2, eval = FALSE}
+gh repo: https://github.com/benmarwick/replicationteachingarchaeology
 # devtools::install_github("ekothe/rmdrive")
@@
 Here we propose a new type of assignment, the replication report, to better align the practice of teaching archaeology with the ideals of archaeological practise.
-The replication report assignment involves students analysing a published report to determine the main claims made by the authors of that report, students obtaining the data used by the authors, and analysing that data to determine if one or more of the authors’ claims are reliable.
+The replication report assignment involves three key steps: 1) students analysing a published report to determine what are the main claims made by the authors of that report, 2) students obtaining the data used by the authors, and 3) analysing that data to determine if one or more of the authors’ claims are reliable.
 
 In this paper we describe how to implement a replication report assignment suitable for upper level undergraduates and graduate students in archaeology.
-Our experience is based on an upper level archaeology class on stone artefact analysis taught at the University of Washington.
+Our experience is based on an upper level archaeology class on stone artefact analysis taught during the spring quarter of 2019 at the University of Washington.
 The class format includes a weekly cycle of lecture, discussion seminar, and hands-on laboratory activities.
 The assignments include seminar notes, lecture quizzes, laboratory worksheets, and two longer empirical reports.
-For the term that we report here, the class had 16 students, a typical number for this class, and similar to the usual size of upper-level laboratory classes in the archaeology program at the University of Washington.
+For the term that we report here, the class had 16 students, and one graduate student teaching assistant.
+THis is a typical size for this class, and similar to the usual size of upper-level laboratory classes in the archaeology program at the University of Washington.
+The background of our students are mostly in humanities with diverse level of statistical knowledge.
 Here we survey the literature on similar types of assignments in other fields to identify common elements that other fields have identified as important principles and skills.
-We describe our assignment and discuss student feedback on the our implementation.
+We describe our assignment and discuss student feedback on our implementation.
 Finally we offer recommendations for how to use replication reports to teach archaeology students.
@@
 
-Definitions of ‘replication’ vary across difference research areas and sometimes confused with ‘reproducibility’.
-Some examples in different fields… Definitions of reproducibility vs replicability are contested, survey a few and then declare we will use the ones from here: http://sites.nationalacademies.org/sites/reproducibility-in-science/index.htm
+What does Barba say about the Ddefinitions of ‘replication’ and ‘reproducibility’? https://arxiv.org/abs/1802.03311 ?
 
-What other fields already do this…
-What journals require replication materials? And what exactly do they require?
-What previous examples of replication assignments in other fields? What do they have in common? What are the typical and unusual elements?
+What are the definitions that we use? http://sites.nationalacademies.org/sites/reproducibility-in-science/index.htm
 
-LY- economics: Ball, R., & Medeiros, N.
-(2012).
-Teaching integrity in empirical research: A protocol for documenting data management and analysis.
-The Journal of Economic Education, 43(2), 182-189.
-https://www.tandfonline.com/doi/abs/10.1080/00220485.2012.659647 https://www.bitss.org/wp-content/uploads/2014/06/teaching-integrity-in-empirical-research-required1.pdf
+What other academic fields value replication? How? By their journals and their teaching methods
 
-HL- international studies: Janz, N.
-(2016).
-Bringing the gold standard into the classroom: replication in university teaching.
-International Studies Perspectives, 17(4), 392-407.
-https://doi.org/10.1111/insp.12104
+What journals require replication materials?
+Answers in https://politicalsciencereplication.wordpress.com/2018/07/14/replication-and-transparency-in-political-science-did-we-make-any-progress/  what materials exactly do they require?
+What do we know about how successful that is?
+Answers in https://www.cambridge.org/core/journals/ps-political-science-and-politics/article/how-are-we-doing-data-access-and-replication-in-political-science/8EE49C7FE45B46F20A50D9271BB3AAC4 and https://www.cambridge.org/core/journals/ps-political-science-and-politics/article/lessons-from-a-decade-of-replications-at-the-quarterly-journal-of-political-science/284B2830BFD99888B42D4CEABC28B9EE
 
-RR - computer networking: Yan, L., & McKeown, N.
-(2017).
-Learning networking by reproducing research results.
-ACM SIGCOMM Computer Communication Review, 47(2), 19-26.
-https://ccronline.sigcomm.org/wp-content/uploads/2017/05/acmdl17-97.pdf
+What previous examples of replication assignments in other fields? ~3-6 sentences to summarise who/what/how/etc. of each one.
 
-LY - neuroscience: Millman, K.
-J., Brett, M., Barnowski, R., & Poline, J.
-B.
-(2018).
-Teaching computational reproducibility for neuroimaging.
-Frontiers in neuroscience, 12, 727.
-https://www.frontiersin.org/articles/10.3389/fnins.2018.00727/full
+What are the typical and unusual elements for replication assignments in other fields?
+
+Other courses in our program at UW do not include this kind of assignment, and they are not common in other programs, to the best of our knowledge.
+We posted to the Society of American Archaeology Teaching Archaeology Interest Group to ask for examples of replication assignments used in teaching archaeology, and received no replies from anyone teaching with replication.
+However, we did receive some offers from researchers willing to share their data for future replication assignments.
+We replied that our assignment required students to find public open data linked to publications, and that privately circulated data would not satisfy our requirements.
 
@@
 
+A brief discussion of our replication report assignment was announced at the beginning of the term to give students background about the purpose and concepts of replication and our expectations.
 Our replication report assignment consisted of three small, graded activities to scaffold the preparation of the final report.
-Each step was separated by one week to give students time to work.
-Submissions for each step were graded as complete/incomplete, with feedback provided individually via the Canvas learning management system, and during class meetings.
+The first step started from week four and each step was separated by one week to give students time to work and submit their final reports due on week seven.
+Students were expected to work in groups of 3-4 people, but submit their assignments for each of the three steps and the final report individually.
+Submissions for each step were graded as complete/incomplete, with feedback provided individually via the Canvas learning management system, and collectively during class meetings.
+Our course had no prerequisites, so we assumed no prior knowledge of R among the students, and were prepared to teach them as complete novices.
+We were also prepared for students to have no prior experience with replication assignments.
 
 For the first step we supplied students with a list of journal articles that included raw data and R code either in supplemental files or deposited on open data repositories.
-This list is updated regularly, but is not exhaustive and is currently online at https://github.com/benmarwick/ctv-archaeology Working in groups of 3-4 people, students selected a journal article from this list as their target article for this assignment.
+This list is updated regularly, but is not exhaustive, and is currently online at https://github.com/benmarwick/ctv-archaeology.
+Working in groups of 3-4 people, students selected a journal article from this list as their target article for this assignment.
 We encouraged them to choose a target article about a stone artefact analysis that looked interesting to them.
 We also required students to set up an open communication channel for their group to ensure they had an easy way to discuss their selection of the target article.
-We used Slack, a free cloud-based web application for team communication.
-The instructors were members of all the student group channels to give guidance and support good communication habits.
+We used Slack, a free cloud-based web application for team communication, to help them collaborate with each other efficiently.
+The instructors were members of all the student group channels to supervise, give guidance and support good communication habits.
 Students were required to individually submit the full bibliographic reference for their target article to complete step one.
@@
 They were told to study the data visualizations in the paper to identify which figures seem to give the best support to the authors' claims.
-Recreating these 1-2 key visualisations was a key task in the production of the final report.
+Recreating these 1-2 visualisations was a key task for the students in the production of their final report.
 A second task for step two was for students to identify and obtain the raw data files of their target article.
 The list of articles that the students chose from only included articles for which data were openly available.
-This removed the need for students to contact authors to request data, which may have added the risk of a long wait, refusal to share, or no reply.
+This removed the need for students to contact authors to request data, which may have added the risk of a long wait for a favourable reply, refusal to share, or no reply.
 To complete step two, each student was required to submit a short statement summarising the 2-3 key claims of their target paper, and the raw data file.
@@
 
-In the time between students submitting their final report and the grades being released we administered an  survey to obtain feedback anonymously from the students.
+In the time between students submitting their final report and the grades being released we administered an online survey on Canvas to obtain feedback anonymously from the students.
 The purpose of the feedback survey was to collect information about how to improve the assignment for future classes, to understand the students’ experience of the assignment, and what value they perceive in replication skills for archaeology in general, and for them individually.
+They had one week to respond survey, which was not a requirement but we encouraged them to give their valuable feedback.
+The anonymous survey before releasing grade of replication assignment could reduce possible biases from subjective perception when knowing grade to ensure a more reliable feedback.
+After the online survey was finished, the instructor showed the results to students in a lecture and invited them to share their thoughts for some interesting observations.
 
@@
 The second step was mostly straightforward, with students engaging in discussion in class and on Slack to identify the 2-3 key claims of their target paper, and identify the data visualisation that provided the most relevant support to one or more of those claims.
+Given that not all students have statistical background, the instructor covered some statistical methods they might encounter while reading during lecture, such as principal components analysis, to give them the mathematical concepts behind it.
 Identifying the data files was less straightforward, with about one third of students failing to correctly identify the data files accompanying their target article.
@@
 Our intention was that two lab classes earlier in the term that introduced students to some methods for data visualization using R would provide the foundation for succeeding in this step.
+We have expected that two accompanying lab reports that required to be written with R markdown would help them practice crucial code they might need later.
+For the lab reports, they used R markdown template we provided to complete tasks of reading data into R, basic data tidying, and data visualization by modifying sample code.
 However, we found that for some students this was not sufficient practice, and substantial instructor guidance was required to help them complete this step.
@@
 
-Our course had no prerequisites, so we assumed no prior knowledge of R among the students, and were prepared to teach them as complete novices.
-We were also prepared for students to have no prior experience with replication report assignments.
-Other courses in our program at UW do not include this kind of assignment, and they are not common in other programs, to the best of our knowledge.
-We posted to the Society of American Archaeology Teaching Archaeology Interest Group to ask for examples of replication reports used in teaching archaeology, and received no replies.
+Thirteen out of sixteen students completed an anonymous feedback survey that includes two single answer questions, five likert scale questions, and two open-ended questions.
+Single answer questions were designed to know students' prior experiences of replication assignment and using R language.
+Ratings for likert scale questions were on a 1 through 5 scale starting at "strongly agree" down to "strongly disagree" to understand students opinion and attitude toward replication assignment in archaeology.
+Two open-ended questions seek to know more about their thoughts for replication in the classroom in general.
 
-```{r}
-library(tidyverse)
-feedback <- read_csv(here::here("analysis/data/raw_data/Replication report feedback Survey Student Analysis Report.csv"))
+Describe the two figures we have for this…
 
-```
+## Analysis of the students' grades for the replication assignment
 
-describe results of follow-up survey: https://canvas.uw.edu/courses/1272207/quizzes/1134059/statistics
+We graded the students’ final submissions using a rubric with criteria that covered content, the introduction, methods, result, and conclusion sections, and style.
+In Figure \@ref(fig:rubric-scores) we show the distribution and means of student scores for each criterion.
+The two criteria showing the highest mean score are “Style: use commas and apostrophes correctly, and spell consistently”, and “Intro: has clear statement of the purpose of the report”.
+All students got a perfect score for these two criteria.
+High scores for the grammar criterion are expected because these reflect basic writing skills required for many undergraduate-level courses.
+Students are expected to have learned these in lower level classes before taking this class.
+The high scores relating to the introduction section may reflect the effectiveness of the scaffolding steps that focussed students on the specific purpose of the assignment .
+The lowest mean score is for “Content: minimum of 4 scholarly items in the reference list” that shows some people did not include four items.
+This might result from insufficient prior training in searching for scholarly publications, suggesting that although this is also a skill that should have been acquired before taking this class, many students remain weak at this task.
+A low mean is also evident for "Intro: has names, locations, and basic chronology of sites", because some students neglected to supply these archaeological details.
+Future use of this assignment will incorporate these low-scoring criteria into the scaffolding steps to emphasize their importance to students and give an opportunity for early feedback to students.
 
-Discussion and conclusion
+The criteria most relevant to the replication component of the assignment, in order from highest mean score to lowest, are "Content: submission includes Rmd file, Data file, and Word file",  "Conclusion: state whether the author’s claims appear to be robust, unreliable, etc","Results: includes 1-2 original plots & description of these", and "Methods: identify the specific results you will replicate".
+This suggests that we could help students to develop a better skills in narrating their process (writing about methods), and describing and interpreting their data visualizations.
+In future we may include more fundamental exercises focusing on these tasks in the scaffolding steps.
+Overall, we find that comparison of the scores for the replication criteria and other criteria shows there is no clear evidence that the replication component of this assignment lowers students’ grades.
+The two lowest scoring criteria are more generic research and writing skills rather than skills specific to the replication aspect of the assignment.
 
-Recommendations… future plans
+Caption: Here is the output from the Canvas grading rubric showing the scores for each student (one dot) and each criterion that we graded the assignment on.
+The red bar shows the mean score for each criterion.
+
+## Discussion
+
+What are the benefits of replication in the classroom?
+
+What are the challenges of replication in the classroom?
+
+What factors could influence the success of replication practice?
+Term, students’ background, familiarity with programming language, basic techniques and statistics teaching in classes, tutorials, choices of papers for replications
+
+## Conclusion
+
+What are our main findings?
+
+What are the limitations of our study?
+Small sample size might affect statistical power, feedback survey as an assessment method might be subjective (comparison with grade ), control conditions: other factors that might have impact on the replication paper
+
+What recommendations can we make to other archaeology instructors?
+Learning motivation, understanding of statistics and principles behind graphs with some exercises
+
+What will we do differently in the future?
+
+## Acknowledgements
 
@@
 ```
-
-________________
-
-Notes:
-
-Target journal: Advances in Archaeological Practice - how to section 3500 words “clear, concise, step-by-step guidelines for successfully completing tasks that are or are becoming common practice”
-
-Key papers to read and cite:
-
-Ball, R., & Medeiros, N.
-(2012).
-Teaching integrity in empirical research: A protocol for documenting data management and analysis.
-The Journal of Economic Education, 43(2), 182-189.
-https://www.bitss.org/wp-content/uploads/2014/06/teaching-integrity-in-empirical-research-required1.pdf
-
-Toelch, U., & Ostwald, D.
-(2018).
-Digital open science—Teaching digital tools for reproducible and transparent research.
-PLoS biology, 16(7), e2006022.
-https://journals.plos.org/plosbiology/article?id=10.1371/journal.pbio.2006022
-
-Medeiros, N., & Ball, R.
-J.
-(2017).
-Teaching Integrity in Empirical Economics: The Pedagogy of Reproducible Science in Undergraduate Education.
-https://scholarship.haverford.edu/cgi/viewcontent.cgi?article=1189&context=economics_facpubs
-
-Hicks, S. C., & Irizarry, R. A. (2018). A guide to teaching data science. The American Statistician, 72(4), 382-391.
-
-Janz, N. (2016). Bringing the gold standard into the classroom: replication in university teaching. International Studies Perspectives, 17(4), 392-407. https://doi.org/10.1111/insp.12104
-
-Jern, A. (2018). A preliminary study of the educational benefits of conducting replications in the classroom. Scholarship of Teaching and Learning in Psychology, 4(1), 64.
-
-Çetinkaya-Rundel, M., & Rundel, C. (2018). Infrastructure and tools for teaching computing throughout the statistical curriculum. The American Statistician, 72(1), 58-65.
-
-Yan, L., & McKeown, N.
-(2017).
-Learning networking by reproducing research results.
-ACM SIGCOMM Computer Communication Review, 47(2), 19-26.
-https://ccronline.sigcomm.org/wp-content/uploads/2017/05/acmdl17-97.pdf
-
-Millman, K.
-J., Brett, M., Barnowski, R., & Poline, J.
-B.
-(2018).
-Teaching computational reproducibility for neuroimaging.
-Frontiers in neuroscience, 12, 727.
-https://www.frontiersin.org/articles/10.3389/fnins.2018.00727/full
-
-Wessa, P. (2009). How Reproducible Research Leads to Non-Rote Learning within Socially Constructivist Statistics Education. Electronic Journal of e-Learning, 7(2), 173-182.
-
-https://politicalsciencereplication.wordpress.com/2014/04/02/reproducibility-pioneers-political-scientists-assigning-replications-to-students/
-
-https://www.washingtonpost.com/news/monkey-cage/wp/2014/02/12/replication-in-political-science-graduate-courses-an-untapped-resource/?noredirect=on&utm_term=.a557ce616b59
-
-https://docs.google.com/forms/d/e/1FAIpQLSeRk7_4Rrzb3DafYGD4NYFjlNJ1rct50iPzzsEuxk6kiID-ag/viewform
-
-Apply for Sloan foundation for a survey and study of data availability https://sloan.org/programs/digital-technology/scholarly-communication https://sloan.org/grants/apply#tab-letters-of-inquiry
-________________
-
-For each case study of a class that uses a replication assignment, we want to know
-
-Variable
-	Ball and Medeiros (2012)
-	Ball (2018)
-	Janz 2016
-	Millman et al.(2018) 
-	Yan & McKeown 2017
-	etc
-	How long (year/term/week)?
-	A term
-
-	8 weeks
-	fall semester, 17 weeks 
-	Three weeks
-
-	How many students?
-	NA
-
-	~15
-
-	200 students over 5 years
-
-	Group or individual?
-	individual
-
-	individual
-	group
-	In pairs
-
-	Main software tool (R/Python/??)?
-	Stata
-
-	R
-	Python
-	Amazon Web Services EC2
-
-	Using Markdown/LaTeX/??
-	NA
-	R Markdown
-	NA
-	Markdown
-	NA
-
-	Using Git/GitHub or not?
-	NA
-
-	NA
-	Git and GitHub
-	NA
-
-	Using CI (e.g. Travis) or not?
-	NA
-
-	NA
-	Travis CI, Circle CI, and Appveyor
-	No
-
-	In class presentation or not?
-	NA
-
-	Yes
-	Yes
-	Yes
-
-	Peer review by other students or not?
-	NA
-
-	Yes
-	Yes
-	Yes
-
-	Students contact original study authors or not?
-	NA
-
-	Yes
-
-	Yes
-
-	Public posting of results by students (e.g. blog, osf.io, other repository) or not?
-	Yes, Haverford College Library
-
-	Yes
-
-	Yes
-
-________________
-
-Notes on the background readings
-
-Ball and Medeiros (2012)
-
-To achieve the goal of fostering and teaching reproducible research, Ball and Medeiros (2012) developed a protocol for documenting statistical analyses for economics undergraduates to use for their empirical research projects.
-Instead of partial replication for final results, their 'soup to nut' approach suggests that the standards of replicability must contain four elements, including raw data files, associated metadata, all commands of data processing and analysis, and public availability.
-This approach establishes norms for complete documentation of empirical research to ensure researchers could successfully reproduce the results by reducing difficulties encountered during replication due to insufficient and partial sharing of data and analytical processes.
-Moreover, the transparency and reproducible of data bring important pedagogical benefits for students at all stages of completing their projects.
-Command files enable students to work with the data more efficient and have better data management by keeping track of each step they have done, and the most importantly, complete documentation of research helps students to take responsibility and accountability for their work.
-
-Janz, Nicole. 2016. “Bringing the Gold Standard into the Classroom: Replication in University Teaching.” International Studies Perspectives 17: 392-407. 
-·     Janz argues for bringing replication assignments into the graduate teaching program of political science
-·     These assignments would do well in methods classes both to train in methods and to teach how to make work reproducible
-·     In some courses for younger students, a duplication may be more beneficial, in upper level classes, a replication where original work is tested, plus new analyses or data can be added and potentially published
-·     Replication studies allow a student to learn with original data, including bugs and flaws and to follow along the logic of the author
-·     Teaches students how to make their own work reproducible in the future
-·     Goes beyond literature review in helping students understand the field
-·     This article addresses some criticisms as well: this does not promote error-hunting, and in fact, it was better for students when there were no errors, it does not hurt the reputation of other scientists, their work should be correct in the first place
-·     Her class was interdisciplinary which she found very valuable for idea sharing, but difficult because people came in with different skill levels
-
-Yan & McKeown (2017)
-* The authors argue that replication assignments in graduate level courses provide more qualitative learning, inspire future research, and improve the networking community
-* Networking graduate students at Stanford learn in a unique top-down manner that encourages them to learn the deeper mechanisms of the Internet
-* Building from that approach, they were asked to create their own projects -- but these were lacking due to the time constraints of a term and overly ambitious projects
-* Instead, students asked to replicate "classic" netowrking papers
-* 200 students over 5 years (2012-2017), 40 unique papers reproduced & projects published on course blog
-* Work emulated in Mininet or Mahimahi (or another emulator if the original authors did so)
-* Students who fail to correctly replicate results are still considered successful if their results resemble the general shape of the original, or if they are able to reflect and identify their own mistakes
-* The "large majority" finished their projects by correctly replicating the original results
-* Peer review and peer replication: pairs will end the assignment by reproducing another pair's replication
-* Primary reason for the project is unique educational and experiential value
-* Recreating the experiment is time consuming but very fulfulling. Students learned the paper much better by immersing themselves in it
-* Unexpectedly, this project contributes to networking community as students verify work or expose inconsistencies 
-* Students acquire new professional skills that they otherwise would not have

### 2019-06-20 analysis/paper/paper.Rmd
get updates from google doc

@@
   - Liying Wang
+  - Ryan Robinson
+  - Hope Loiselle
 date: "`r format(Sys.time(), '%d %B, %Y')`"
@@
 
-In many research communities there are changes underway that promote or require high levels of transparency and reproducibility of research.
-For example...
-using open source programming language such as R or Python...
-
-Archaeologists are increasingly adopting these practices also.
-For example… However current norms in teaching archaeology are out of step with these practices.
-Given shifts in community values, it is important that we prepare our students with the skills necessary to fulfill these expectations of greater transparency and reproducibility in research.
-Here we propose a new type of assignment, the replication report, to better align the practice of teaching archaeology with the ideals of archaeological practise.
+In his influential study of replication, sociologist of science Harry Collins argued that replication is at the core of scientific practice, writing “Replicability [...] is the Supreme Court of the scientific system” (Collins 1985: 19).
+Like other observers of science, Collins claimed that in replication, private observations become communal facts, offering vital protection from error and fraud.
+In this paper we propose a new type of assignment for the archaeology classroom, the replication report, to better align the practice of teaching archaeology with the transparency and openness ideals of science (Nosek et al 2015).
 The replication report assignment involves three key steps: 1) students analysing a published report to determine what are the main claims made by the authors of that report, 2) students obtaining the data used by the authors, and 3) analysing that data to determine if one or more of the authors’ claims are reliable.
 
-In this paper we describe how to implement a replication report assignment suitable for upper level undergraduates and graduate students in archaeology.
-Our experience is based on an upper level archaeology class on stone artefact analysis taught during the spring quarter of 2019 at the University of Washington.
+We describe how to implement a replication report assignment suitable for upper level undergraduates and graduate students in archaeology.
+Our experience is based on an upper level archaeology class on stone artefact analysis taught during the Spring quarter of 2019 at the University of Washington.
 The class format includes a weekly cycle of lecture, discussion seminar, and hands-on laboratory activities.
@@
 For the term that we report here, the class had 16 students, and one graduate student teaching assistant.
-THis is a typical size for this class, and similar to the usual size of upper-level laboratory classes in the archaeology program at the University of Washington.
-The background of our students are mostly in humanities with diverse level of statistical knowledge.
+This is a typical size for this class, and similar to the usual size of upper-level laboratory classes in the archaeology program at the University of Washington.
+Our students are mostly in social science and humanities majors with diverse levels of statistical knowledge.
 Here we survey the literature on similar types of assignments in other fields to identify common elements that other fields have identified as important principles and skills.
 We describe our assignment and discuss student feedback on our implementation.
-Finally we offer recommendations for how to use replication reports to teach archaeology students.
+Finally, we offer recommendations for how to use replication reports to teach archaeology students.
 
-## Background
+## What is replication?
 
-What does Barba say about the Ddefinitions of ‘replication’ and ‘reproducibility’? https://arxiv.org/abs/1802.03311 ?
+Barba (2018) points out that there is confusion and conflicting uses of the terms "reproducibility" and "replication" in recent years.
+In her survey of relevant literature from many disciplines, Barba finds that some fields make no distinction between "reproducibility" and "replication", and among fields that do recognise a distinction between the two, the meanings are sometimes directly swapped from one discipline to another.
+Here we follow what Barba has identified as the most common, long-established and highly cited definitions of these terms, and these are also the same as recently recommended by the National Academies of Sciences, Engineering, and Medicine (2019).
+Reproducibility is the ability to obtain results by using the same data, code, and procedures provided by the original authors (cf.
+Marwick 2017).
+This is only possible when the authors make all those materials available, for example in a research compendium (Marwick et al.
+2018, Gentleman and Temple Lang 2007).
+Replication is the ability to arrive at the same scientific conclusions in a new study, collecting new data (possibly with different methods) and completing new analyses.
 
-What are the definitions that we use? http://sites.nationalacademies.org/sites/reproducibility-in-science/index.htm
+In the following section we briefly survey replication assignments described in other fields to survey the variety of forms this usually takes.
+Replication assignments across different fields may not strictly fit into the above definition of replication because they do not always involve a completely new study.
+We consider that if a study departs from any of the original materials e.g.
+new data with previously published code, or new code with previously published data, then it is broadly within the definition of replication.
 
-What other academic fields value replication? How? By their journals and their teaching methods
+## How do different disciplines use replication assignments?
 
-What journals require replication materials?
-Answers in https://politicalsciencereplication.wordpress.com/2018/07/14/replication-and-transparency-in-political-science-did-we-make-any-progress/  what materials exactly do they require?
-What do we know about how successful that is?
-Answers in https://www.cambridge.org/core/journals/ps-political-science-and-politics/article/how-are-we-doing-data-access-and-replication-in-political-science/8EE49C7FE45B46F20A50D9271BB3AAC4 and https://www.cambridge.org/core/journals/ps-political-science-and-politics/article/lessons-from-a-decade-of-replications-at-the-quarterly-journal-of-political-science/284B2830BFD99888B42D4CEABC28B9EE
+Some of the earliest discussions of replication in university curricula appear in economics and psychology.
+Ball and Medeiros (2012) describe their TIER (teaching integrity in empirical research) protocol for undergraduate economics students at Haverford College.
+This is intended to ensure that a student's work is replicable by the instructors.
+Their protocol requires that when students submit their final project report, their submission must contain four elements: the raw data files, a metadata file, script files of code used to analyse the data, and public availability (i.e.
+deposit on an open repository such as Dataverse).
+Frank and Saxe (2012) describe how they teach undergraduates (at MIT) and graduate students (at Stanford) to do in-class replications of recent, cutting-edge psychology experiments, and note that several projects from their undergraduate course have even been part of successful publications.
+More recently Hawkins et al.
+(2018) reported on 11 replication assignments from a psychology graduate seminar at Stanford, finding that the replications typically yielded effects that were smaller than the originally published ones.
+Similarly, Jern (2018) describes how students in a psychology course completed replication assignments by using statistical methods of the original research articles with new data collected by the students outside of class.
 
-What previous examples of replication assignments in other fields? ~3-6 sentences to summarise who/what/how/etc. of each one.
+Students in Stanford University’s graduate course ‘Advanced Topics in Networking’ are given a replication assignment in which they are asked to replicating “classic” computer networking experiments (Yan and McKeown 2017).
+Students work in pairs and receive modest instructor support.
+The assignment entails selecting appropriate emulation software, communicating with the original authors, obtaining the authors’ materials, replicating the experiment, and publicising their results through both an in-class presentation and a blog post on a program website.
+We classify this as a replication assignment because many students could not obtain the original code from the authors, and had to write their own for the assignment.
+Since 2012, over 200 undergraduate and graduate students have participated in this assignment with an 86% success rate (Yan and McKeown 2017).
+Student feedback suggests high satisfaction with the assignment, citing unique educational value, improved understanding of the original material, and the acquisition of professional skills.
+In some cases, students personally contributed to the network engineering literature when their replications exposed inaccuracies in original experiments, which were then presented to and publicly amended by the authors (Yan and McKeown 2017).
 
-What are the typical and unusual elements for replication assignments in other fields?
+In describing her political science classes at the University of Cambridge, Janz (2016) argues that reproducibility and replication should be held as the gold standard for scientific research.
+She claims that teaching these concepts should be a necessary component of graduate studies, to ensure students can make their own future work reproducible.
+Janz reports on her class in which about 15 students undertake replication assignments over eight weeks, including providing weekly updates to each other to gain insight and feedback.
+Janz describes two possible levels of assignment suitable for different lengths of the term and levels of the students: duplication (aiming for the exact same results based on the exact same data set with exactly the same methods) and replication (tests the robustness of previous research results by employing newly collected data, and/or new variables, and/ or new model specifications).
+Duplication, which we would define here as reproduction, may be beneficial for lower-level students, while upper-level students can replicate a study and contribute original data, potentially leading to publication.
+Janz (2016) describes how replication assignments are a growing trend in political science departments (noting that R and STATA are commonly used), and reviews many of the practical challenges of doing replication assignments in a graduate course.
+She also responds to six typical criticisms of replication assignments, and points out the need for universities to nurture a culture of reproducibility and replication to ensure that the gold standard of reliable, credible, and valid research is not just an empty phrase.
 
-Other courses in our program at UW do not include this kind of assignment, and they are not common in other programs, to the best of our knowledge.
-We posted to the Society of American Archaeology Teaching Archaeology Interest Group to ask for examples of replication assignments used in teaching archaeology, and received no replies from anyone teaching with replication.
-However, we did receive some offers from researchers willing to share their data for future replication assignments.
-We replied that our assignment required students to find public open data linked to publications, and that privately circulated data would not satisfy our requirements.
+The Freie Universität Berlin extracurricular graduate seminar course “Digital Open Science” aims to teach open science practice and assigns replication projects, mostly around neuroimaging topics (Toelch and Ostwald 2018).
+These projects are carried out with a variety of typical open science software tools and services, including Python, R, Git, GitHub and the Open Science Framework.
+Students first receive extensive lectures and hands-on tutoring, then choose a simple neuroscience experiment to replicate.
+Finally, they present their results at a symposium.
+The course’s primary goal is to teach students the value of verifying data upon which their own future research might rely.
+Students report a high rate of engaging in open science practices after taking the class, and 80% of the participants said that they believe the open science techniques will improve their future research as professionals (Toelch and Ostwald 2018).
+Millman et al (2018) describe a similar course at Berkeley that teaches students how to use open science tools to complete a capstone replication assignment on neuroscience topics.
 
-## Methods
+This brief survey demonstrates that replication assignments are widely known in economics, psychology, political science, and neuroscience.
+Common elements include group work, use of open science software and services to make the replication results openly accessible to anyone, and a scaffolded, stepwise approach to the task to ensure that students receive instructor support at multiple stages in the assignment.
+To the best of our knowledge replication assignments are not common in archaeology programs.
+We posted a message to the Society of American Archaeology Teaching Archaeology Interest Group e-community to ask for examples of replication assignments used in teaching archaeology, and received no replies from anyone teaching with replication.
 
-A brief discussion of our replication report assignment was announced at the beginning of the term to give students background about the purpose and concepts of replication and our expectations.
+## How to conduct a replication assignment in archaeology
+
+In this section we describe our replication assignment and how we assessed its effectiveness.
+A brief discussion of our replication report assignment was announced at the beginning of the ten week-long term to give students background about the purpose and concepts of replication and our expectations.
 Our replication report assignment consisted of three small, graded activities to scaffold the preparation of the final report.
-The first step started from week four and each step was separated by one week to give students time to work and submit their final reports due on week seven.
+The first step started from Week Four and each step was separated by one week to give students time to work and submit their final reports due on Week Seven.
 Students were expected to work in groups of 3-4 people, but submit their assignments for each of the three steps and the final report individually.
 Submissions for each step were graded as complete/incomplete, with feedback provided individually via the Canvas learning management system, and collectively during class meetings.
-Our course had no prerequisites, so we assumed no prior knowledge of R among the students, and were prepared to teach them as complete novices.
+Our course had no prerequisites, so we assumed no prior knowledge of the R programming language among the students, and were prepared to teach them as complete novices.
+We chose R (R Core Team 2019) because it is widely used by archaeologists (Schimdt and Marwick 2019), and also commonly taught in undergraduate classes in social sciences and statistics (Baumer et al.
+2014; Çetinkaya-Rundel and Rundel 2018; Dvorak et al 2019).
 We were also prepared for students to have no prior experience with replication assignments.
+
+### Step 1: In groups, select a study to replicate
 
@@
 We also required students to set up an open communication channel for their group to ensure they had an easy way to discuss their selection of the target article.
-We used Slack, a free cloud-based web application for team communication, to help them collaborate with each other efficiently.
+We used Slack (https://slack.com/, Perkel 2016), a free cloud-based web application for team communication, to help them collaborate with each other efficiently.
 The instructors were members of all the student group channels to supervise, give guidance and support good communication habits.
@@
 
+### Step 2: Identify the key claims and data in the study
+
 For step two of the assignment, students were required to discuss in their groups to identify 2-3 key claims made by the authors of their target article.
-They were told to study the data visualizations in the paper to identify which figures seem to give the best support to the authors' claims.
+They were told to study the data visualisations in the paper to identify which figures seem to give the best support to the authors' claims.
 Recreating these 1-2 visualisations was a key task for the students in the production of their final report.
@@
 
-Step three of the assignment required students to create a file structure on their computer to organise their assignment files, to download an R Markdown file and write a small amount of R code to read in the raw data and explore it with one basic visualisation, unrelated to any in the target article.
-We prepared an R Markdown file with some basic headings (following the IMRaD or  Introduction-Method-Results-and-Discussion format) and empty code chunks to provide guidance on how many code chunks were expected, and where in the document they should appear.
+### Step 3: Begin the replication analysis and get instructor feedback
+
+Step three of the assignment required students to create a file structure on their computer to organise their assignment files, following basic guidance in Marwick et al.
+(2017).
+They also had to download an R Markdown file and write a small amount of R code to read in the raw data and explore it with one basic visualisation, using data in the target article.
+R Markdown is a file format for making reproducible documents with R.
+An R Markdown document is written in markdown (a simple plain text format) and contains chunks of embedded R code (Xie et Al.
+2018).
+The document can be easily converted into many standard formats, such as Microsoft Word, PDF and HTML.
+We prepared an R Markdown template file with some basic headings (following the IMRaD or  Introduction-Method-Results-and-Discussion format) and empty code chunks to provide guidance to the students on how many code chunks were expected, and where in the document they should appear.
 As students wrote their R code and encountered errors, they were encouraged to share screenshots on Slack for the instructors to assist with troubleshooting.
 After completing this step, the instructor met with each group to review the main claims identified by the students, review the visualisation they had chosen to replicate, and provide guidance on writing the R code to produce the key visualisations.
+
+### Step 4: Complete the replication analysis and submit the compendium of report, code and data
 
@@
 Microsoft Word document that is produced when they knit the R Markdown file).
-Our expectation was that we could create any student’s results by running their submitted R Markdown document and the raw data file to produce the Word document they submitted.
+Our expectation was that we could reproduce any student’s results by running their submitted R Markdown document with the raw data file to produce the Word document they submitted.
 The final report was graded with a rubric which was presented to the students at the first step to help set expectations about what the final product should look like.
@@
 The purpose of the feedback survey was to collect information about how to improve the assignment for future classes, to understand the students’ experience of the assignment, and what value they perceive in replication skills for archaeology in general, and for them individually.
-They had one week to respond survey, which was not a requirement but we encouraged them to give their valuable feedback.
-The anonymous survey before releasing grade of replication assignment could reduce possible biases from subjective perception when knowing grade to ensure a more reliable feedback.
-After the online survey was finished, the instructor showed the results to students in a lecture and invited them to share their thoughts for some interesting observations.
+Two questions were designed to learn about students' prior experiences of replication assignment and using the R language.
+We asked about students’ opinions and attitudes toward replication assignments in archaeology and collected responses on a likert scale.
+Two open-ended questions sought to know more about the students’ thoughts on replication in the classroom in general.
+They had one week to respond to the survey, which was not a requirement.
 
-## Results
-
-### Observations on the assignment process
+## Observations on the assignment process
 
@@
 The ability to easily share screenshots on Slack was important to the success of the third step.
-Our intention was that two lab classes earlier in the term that introduced students to some methods for data visualization using R would provide the foundation for succeeding in this step.
-We have expected that two accompanying lab reports that required to be written with R markdown would help them practice crucial code they might need later.
-For the lab reports, they used R markdown template we provided to complete tasks of reading data into R, basic data tidying, and data visualization by modifying sample code.
+Our intention was that two lab classes earlier in the term that introduced students to some methods for data visualisation using R would provide the foundation for succeeding in this step.
+We have expected that two lab reports completed earlier in the term that required to be written with R markdown would help them practice crucial code they might need later.
+For the lab reports, students used R markdown templates we provided to complete tasks of reading data into R, basic data tidying, and data visualisation by modifying sample code.
 However, we found that for some students this was not sufficient practice, and substantial instructor guidance was required to help them complete this step.
-At the completion of this step, the instructor met one on one with each group to check how successful they were producing a basic visualization using data from the target article, and to discuss the group's strategy to complete the report.
+At the completion of this step, the instructor met one on one with each group to check how successful they were producing a basic visualisation using data from the target article, and to discuss the group's strategy to complete the report.
 This was the most time-consuming aspect of the assignment for the instructor, holding a one hour meeting with each of the five groups.
@@
 
-Thirteen out of sixteen students completed an anonymous feedback survey that includes two single answer questions, five likert scale questions, and two open-ended questions.
-Single answer questions were designed to know students' prior experiences of replication assignment and using R language.
-Ratings for likert scale questions were on a 1 through 5 scale starting at "strongly agree" down to "strongly disagree" to understand students opinion and attitude toward replication assignment in archaeology.
-Two open-ended questions seek to know more about their thoughts for replication in the classroom in general.
+Thirteen out of sixteen students completed an anonymous feedback survey (Figure X).
+Only one student had done replication before and two had used R previously for an archaeology assignment.
+Most students strongly agreed with the statements about having sufficient support and clear instructions.
+Most students strongly disagreed with the statement, “I am likely to attempt to replicate published research in my future studies and work”.
+This contrasts with the high proportion of students that agree with the statement “The ability to replicate published research is an important skill for professional archaeologists”.
+Taken together, these two responses show that while students see the value of replication to archaeology in general, they do not see any specific benefits to doing it themselves.
+This may reflect a failure of the instructor to communicate the individual benefits of developing skills for replication.
+It may also reflect uncertainty among the students about their plans for a career in archaeology.
+Most, but not all, students agreed that the replication assignment helped them to learn more effectively than reading a paper to write a traditional paper.
 
-Describe the two figures we have for this…
+Figure X shows the correlations between the five feedback questions that have likert scale responses.
+The statements about instructions and instructor support are highly positively correlated, showing the positive effects of the assignment design, a detailed rubric, and the instructor meeting with each group to discuss their work, and answering students’ questions promptly on Slack.
+The strongest negative correlation is between the statements about instructor support and doing replication in future work.
+This might suggest that the students received so much support that they do not feel capable to do a replication like this by themselves.
+We see confirmation of this in the free-form comments, such as ‘it would not have been possible for us to do this correctly on our own’.
+These correlations indicate a need to equip students with skills to work more independently of the instructor, and strengthen students’ self-efficacy with replication skills.
 
@@
 The two criteria showing the highest mean score are “Style: use commas and apostrophes correctly, and spell consistently”, and “Intro: has clear statement of the purpose of the report”.
-All students got a perfect score for these two criteria.
 High scores for the grammar criterion are expected because these reflect basic writing skills required for many undergraduate-level courses.
 Students are expected to have learned these in lower level classes before taking this class.
-The high scores relating to the introduction section may reflect the effectiveness of the scaffolding steps that focussed students on the specific purpose of the assignment .
+The high scores relating to the introduction section may reflect the effectiveness of the scaffolding steps that focused students on the specific purpose of the assignment.
 The lowest mean score is for “Content: minimum of 4 scholarly items in the reference list” that shows some people did not include four items.
@@
 
-The criteria most relevant to the replication component of the assignment, in order from highest mean score to lowest, are "Content: submission includes Rmd file, Data file, and Word file",  "Conclusion: state whether the author’s claims appear to be robust, unreliable, etc","Results: includes 1-2 original plots & description of these", and "Methods: identify the specific results you will replicate".
+The criteria most relevant to the replication component of the assignment, in order from highest mean score to lowest, are "Content: submission includes Rmd file, Data file, and Word file",  "Conclusion: state whether the author’s claims appear to be robust, unreliable, etc", "Results: includes 1-2 original plots & description of these", and "Methods: identify the specific results you will replicate".
 This suggests that we could help students to develop a better skills in narrating their process (writing about methods), and describing and interpreting their data visualizations.
-In future we may include more fundamental exercises focusing on these tasks in the scaffolding steps.
+In the future we may include more fundamental exercises focusing on these tasks in the scaffolding steps.
 Overall, we find that comparison of the scores for the replication criteria and other criteria shows there is no clear evidence that the replication component of this assignment lowers students’ grades.
@@
 
-Caption: Here is the output from the Canvas grading rubric showing the scores for each student (one dot) and each criterion that we graded the assignment on.
-The red bar shows the mean score for each criterion.
-
 ## Discussion
 
-What are the benefits of replication in the classroom?
+Replication of results is widely claimed as a gold standard in science.
+When a result can be independently validated, we can build on it to advance knowledge in our field.
+Teaching students about replication and giving them skills to conduct replication is thus a vital part of preparing them for professional work in scientific archaeology.
+The immediate practical benefits of students doing replication assignments include realistic experience with analysing and visualising real-word data (rather than toy datasets often used for class activities), and getting them working at the research frontier by taking an in-depth look at recently published work, going beyond the usual reading and discussion.
 
-What are the challenges of replication in the classroom?
+The longer term practical benefits include cultivating a reproducibility routine for students to develop a natural habit of organising their code and data for future work so another person can use it to reproduce their results.
+Benefits also include developing professionalism among students: by working through the steps of an analysis students gain an understanding of what kinds of decisions in all steps of an analysis are acceptable (Janz 2018).
+Although the small scale of our assignment did not offer the potential for students to publish new findings from replication, we anticipate this may be a benefit for archaeology students participating in more extensive replication assignments.
 
-What factors could influence the success of replication practice?
-Term, students’ background, familiarity with programming language, basic techniques and statistics teaching in classes, tutorials, choices of papers for replications
+The challenges of requiring students to do replication assignments are similar to those faced in many types of archaeology classes with quantitative skills at their core.
+In our case, the absence of a prerequisite and the high variability of statistical and programming skills meant that some students needed a lot more support than others.
+This may make replication assignments impractical where instructor-student contact hours are limited.
+In addition to time, the instructor needs to have a high skill level in quantitative methods to guide students in their engagement with the literature.
+The instructor will also benefit from a high tolerance for helping students to solve coding problems.
+To mitigate this in the future we will add a step of student peer review to give students an opportunity to get feedback and assistance from each other more formally.
 
 ## Conclusion
+
+Our main finding is that replication assignments are valued and in common use throughout the social sciences, and that they can be effective in teaching archaeology.
+Specifically, we found it possible to conduct a small scale replication assignment as part of an upper level undergraduate class.
+Student feedback was positive
 
@@
 What are the limitations of our study?
-Small sample size might affect statistical power, feedback survey as an assessment method might be subjective (comparison with grade ), control conditions: other factors that might have impact on the replication paper
+Small sample size might affect statistical power, feedback survey as an assessment method might be subjective (comparison with grade ), control conditions: other factors that might have an impact on the replication paper
 
@@
 
-Table and Figures:
-
-Survey of replication report assignments in other fields
-Instructions to students
-Grading rubric
-R Markdown template snippet 
-Feedback survey facet plot
-
 <!-- The following line inserts a page break when the output is MS Word. For page breaks in PDF, use \newpage on its own line.  -->
@@
 <div id="refs"></div>
+
+Nosek, B. A., Alter, G., Banks, G. C., Borsboom, D., Bowman, S. D., Breckler, S. J., ... & Contestabile, M. (2015). Promoting an open research culture. Science, 348(6242), 1422-1425.
+
+Cliangirig Order: Replication arid Induction in Scientific Practice. BY H. M.
+COLLINS. London, Beverly Hills, and New Delhi: Sage Publications, 1985.
+Pp. viii -+ 187.
+
+Marwick, B. (2017). Computational reproducibility in archaeological research: basic principles and a case study of their implementation. Journal of Archaeological Method and Theory, 24(2), 424-450.
+
+Xie, Y., Allaire, J. J., & Grolemund, G. (2018). R markdown: The definitive guide. CRC Press.
+
+@Manual{,
+  title        = {R: A Language and Environment for Statistical
+                  Computing},
+  author       = {{R Core Team}},
+  organization = {R Foundation for Statistical Computing},
+  address      = {Vienna, Austria},
+  year         = YEAR,
+  url          = {https://www.R-project.org}
+}
+where YEAR is
 

### 2019-06-20 analysis/paper/paper.Rmd
travis and docker

@@
 output: 
-    bookdown::html_document2:
+    bookdown::word_document2:
       fig_caption: yes
@@
 
-In his influential study of replication, sociologist of science Harry Collins argued that replication is at the core of scientific practice, writing “Replicability [...] is the Supreme Court of the scientific system” (Collins 1985: 19).
+In his influential study of replication, sociologist of science Harry Collins argued that replication is at the core of scientific practice, writing “Replicability [...] is the Supreme Court of the scientific system” [@collins1992changing p.
+19].
 Like other observers of science, Collins claimed that in replication, private observations become communal facts, offering vital protection from error and fraud.
-In this paper we propose a new type of assignment for the archaeology classroom, the replication report, to better align the practice of teaching archaeology with the transparency and openness ideals of science (Nosek et al 2015).
+In this paper we propose a new type of assignment for the archaeology classroom, the replication report, to better align the practice of teaching archaeology with the transparency and openness ideals of science [@nosek2015promoting].
 The replication report assignment involves three key steps: 1) students analysing a published report to determine what are the main claims made by the authors of that report, 2) students obtaining the data used by the authors, and 3) analysing that data to determine if one or more of the authors’ claims are reliable.
@@
 
+To enable re-use of our materials and improve reproducibility and transparency according to the principles outlined in @marwick2017open, we include all our assingment materials, as well as the entire R code used for all the analysis and visualizations contained in this paper, in our compendium at http://doi.org/10.17605/OSF.IO/DBSW9.
+Also in this version-controlled compendium are the raw data for the analyses reported here.
+The figures and results presented here can be independently reproduced with the code and data in this repository.
+In our compendium our code is released under the MIT licence, our data as CC-0, and our figures and assingment materials as CC-BY, to enable maximum re-use [for more details, see @Marwick2017].
+
 ## What is replication?
 
-Barba (2018) points out that there is confusion and conflicting uses of the terms "reproducibility" and "replication" in recent years.
+@barba2018terminologies points out that there is confusion and conflicting uses of the terms "reproducibility" and "replication" in recent years.
 In her survey of relevant literature from many disciplines, Barba finds that some fields make no distinction between "reproducibility" and "replication", and among fields that do recognise a distinction between the two, the meanings are sometimes directly swapped from one discipline to another.
 Here we follow what Barba has identified as the most common, long-established and highly cited definitions of these terms, and these are also the same as recently recommended by the National Academies of Sciences, Engineering, and Medicine (2019).
-Reproducibility is the ability to obtain results by using the same data, code, and procedures provided by the original authors (cf.
-Marwick 2017).
-This is only possible when the authors make all those materials available, for example in a research compendium (Marwick et al.
-2018, Gentleman and Temple Lang 2007).
+Reproducibility is the ability to obtain results by using the same data, code, and procedures provided by the original authors [@Marwick2017].
+This is only possible when the authors make all those materials available, for example in a research compendium [@marwick2018packaging].
 Replication is the ability to arrive at the same scientific conclusions in a new study, collecting new data (possibly with different methods) and completing new analyses.
@@
 
-Some of the earliest discussions of replication in university curricula appear in economics and psychology.
-Ball and Medeiros (2012) describe their TIER (teaching integrity in empirical research) protocol for undergraduate economics students at Haverford College.
+Some of the earliest discussions of replication in university curricula appear in economics and psychology [@hoffler2013teaching; @standing2014using].
+@Ball_Medeiros_2012 describe their TIER (teaching integrity in empirical research) protocol for undergraduate economics students at Haverford College.
 This is intended to ensure that a student's work is replicable by the instructors.
@@
 deposit on an open repository such as Dataverse).
-Frank and Saxe (2012) describe how they teach undergraduates (at MIT) and graduate students (at Stanford) to do in-class replications of recent, cutting-edge psychology experiments, and note that several projects from their undergraduate course have even been part of successful publications.
-More recently Hawkins et al.
-(2018) reported on 11 replication assignments from a psychology graduate seminar at Stanford, finding that the replications typically yielded effects that were smaller than the originally published ones.
-Similarly, Jern (2018) describes how students in a psychology course completed replication assignments by using statistical methods of the original research articles with new data collected by the students outside of class.
+@frank2012teaching describe how they teach undergraduates (at MIT) and graduate students (at Stanford) to do in-class replications of recent, cutting-edge psychology experiments, and note that several projects from their undergraduate course have even been part of successful publications.
+More recently @hawkins2018improving reported on 11 replication assignments from a psychology graduate seminar at Stanford, finding that the replications typically yielded effects that were smaller than the originally published ones.
+Similarly, @jern2018preliminary describes how students in a psychology course completed replication assignments by using statistical methods of the original research articles with new data collected by the students outside of class.
 
-Students in Stanford University’s graduate course ‘Advanced Topics in Networking’ are given a replication assignment in which they are asked to replicating “classic” computer networking experiments (Yan and McKeown 2017).
+Students in Stanford University’s graduate course ‘Advanced Topics in Networking’ are given a replication assignment in which they are asked to replicating 'classic' computer networking experiments [@yan2017learning].
 Students work in pairs and receive modest instructor support.
@@
 We classify this as a replication assignment because many students could not obtain the original code from the authors, and had to write their own for the assignment.
-Since 2012, over 200 undergraduate and graduate students have participated in this assignment with an 86% success rate (Yan and McKeown 2017).
+Since 2012, over 200 undergraduate and graduate students have participated in this assignment with an 86% success rate [@yan2017learning].
 Student feedback suggests high satisfaction with the assignment, citing unique educational value, improved understanding of the original material, and the acquisition of professional skills.
-In some cases, students personally contributed to the network engineering literature when their replications exposed inaccuracies in original experiments, which were then presented to and publicly amended by the authors (Yan and McKeown 2017).
+In some cases, students personally contributed to the network engineering literature when their replications exposed inaccuracies in original experiments, which were then presented to and publicly amended by the authors [@yan2017learning].
 
-In describing her political science classes at the University of Cambridge, Janz (2016) argues that reproducibility and replication should be held as the gold standard for scientific research.
+In describing her political science classes at the University of Cambridge, @janz2016bringing argues that reproducibility and replication should be held as the gold standard for scientific research.
 She claims that teaching these concepts should be a necessary component of graduate studies, to ensure students can make their own future work reproducible.
@@
 Duplication, which we would define here as reproduction, may be beneficial for lower-level students, while upper-level students can replicate a study and contribute original data, potentially leading to publication.
-Janz (2016) describes how replication assignments are a growing trend in political science departments (noting that R and STATA are commonly used), and reviews many of the practical challenges of doing replication assignments in a graduate course.
+@janz2016bringing describes how replication assignments are a growing trend in political science departments (noting that R and STATA are commonly used), and reviews many of the practical challenges of doing replication assignments in a graduate course.
 She also responds to six typical criticisms of replication assignments, and points out the need for universities to nurture a culture of reproducibility and replication to ensure that the gold standard of reliable, credible, and valid research is not just an empty phrase.
 
-The Freie Universität Berlin extracurricular graduate seminar course “Digital Open Science” aims to teach open science practice and assigns replication projects, mostly around neuroimaging topics (Toelch and Ostwald 2018).
+The Freie Universität Berlin extracurricular graduate seminar course 'Digital Open Science' aims to teach open science practice and assigns replication projects, mostly around neuroimaging topics [@toelch2018digital].
 These projects are carried out with a variety of typical open science software tools and services, including Python, R, Git, GitHub and the Open Science Framework.
@@
 The course’s primary goal is to teach students the value of verifying data upon which their own future research might rely.
-Students report a high rate of engaging in open science practices after taking the class, and 80% of the participants said that they believe the open science techniques will improve their future research as professionals (Toelch and Ostwald 2018).
+Students report a high rate of engaging in open science practices after taking the class, and 80% of the participants said that they believe the open science techniques will improve their future research as professionals [@toelch2018digital].
 Millman et al (2018) describe a similar course at Berkeley that teaches students how to use open science tools to complete a capstone replication assignment on neuroscience topics.
 
-This brief survey demonstrates that replication assignments are widely known in economics, psychology, political science, and neuroscience.
+This brief survey demonstrates that replication assignments are widely known in economics, psychology, political science, neuroscience and other fields [e.g.
+@roettger2018towards] .
 Common elements include group work, use of open science software and services to make the replication results openly accessible to anyone, and a scaffolded, stepwise approach to the task to ensure that students receive instructor support at multiple stages in the assignment.
 To the best of our knowledge replication assignments are not common in archaeology programs.
-We posted a message to the Society of American Archaeology Teaching Archaeology Interest Group e-community to ask for examples of replication assignments used in teaching archaeology, and received no replies from anyone teaching with replication.
+We posted a message to the Society of American Archaeology Teaching Archaeology Interest Group e-community on 27 May 2019 to ask for examples of replication assignments used in teaching archaeology, and received no replies from anyone teaching with replication.
 
@@
 Our course had no prerequisites, so we assumed no prior knowledge of the R programming language among the students, and were prepared to teach them as complete novices.
-We chose R (R Core Team 2019) because it is widely used by archaeologists (Schimdt and Marwick 2019), and also commonly taught in undergraduate classes in social sciences and statistics (Baumer et al.
-2014; Çetinkaya-Rundel and Rundel 2018; Dvorak et al 2019).
+We chose R [@R_core_team] because it is widely used by archaeologists [@Schmidt2019], and also commonly taught in undergraduate classes in social sciences and statistics [@baumer2014r; @ccetinkaya2018infrastructure; @dvorak2019efficient].
 We were also prepared for students to have no prior experience with replication assignments.
@@
 We also required students to set up an open communication channel for their group to ensure they had an easy way to discuss their selection of the target article.
-We used Slack (https://slack.com/, Perkel 2016), a free cloud-based web application for team communication, to help them collaborate with each other efficiently.
+We used Slack (https://slack.com/), a free cloud-based web application for team communication [@perkel2017scientists], to help them collaborate with each other efficiently.
 The instructors were members of all the student group channels to supervise, give guidance and support good communication habits.
@@
 
-Step three of the assignment required students to create a file structure on their computer to organise their assignment files, following basic guidance in Marwick et al.
-(2017).
+Step three of the assignment required students to create a file structure on their computer to organise their assignment files, following basic guidance in @marwick2018packaging.
 They also had to download an R Markdown file and write a small amount of R code to read in the raw data and explore it with one basic visualisation, using data in the target article.
 R Markdown is a file format for making reproducible documents with R.
-An R Markdown document is written in markdown (a simple plain text format) and contains chunks of embedded R code (Xie et Al.
-2018).
+An R Markdown document is written in markdown (a simple plain text format) and contains chunks of embedded R code [@xie2018r].
 The document can be easily converted into many standard formats, such as Microsoft Word, PDF and HTML.
@@
 
-Thirteen out of sixteen students completed an anonymous feedback survey (Figure X).
+```{r plot-feedback-survey}
+library(knitr)
+read_chunk("plot-feedback-survey.R")
+```
+
+```{r prepare-the-feedback-data}
+
+```
+
+```{r plot-the-feedback-data}
+
+```
+
+```{r show-plot-feedback, fig.cap = "Results of the anonymous feedback survey on the replication assignment"}
+include_graphics(here::here("analysis/figures/feedback_likert_yn_plot.png"))
+```
+
+Thirteen out of sixteen students completed an anonymous feedback survey (Figure \@ref(fig:show-plot-feedback)).
 Only one student had done replication before and two had used R previously for an archaeology assignment.
@@
 
-Figure X shows the correlations between the five feedback questions that have likert scale responses.
+```{r show-plot-feedback-correlations, fig.cap = "Correlations among feedback items with Likert scale responses.
+The size of the dot indicates the magnitude of the correlation, and the colour indicates the direction (red is negative, blue is positive).
+Correlations were computed using Spearman's method."}
+include_graphics(here::here("analysis/figures/feedback_likert_corr.png"))
+```
+
+Figure \@ref(fig:show-plot-feedback-correlations) shows the correlations between the five feedback questions that have likert scale responses.
 The statements about instructions and instructor support are highly positively correlated, showing the positive effects of the assignment design, a detailed rubric, and the instructor meeting with each group to discuss their work, and answering students’ questions promptly on Slack.
@@
 
+```{r plot-rubric}
+library(knitr)
+read_chunk("plot-rubric-scores.R")
+```
+
+```{r  prepare-the-rubric-data}
+
+```
+
+```{r plot-the-rubric-data}
+
+```
+
+```{r show-plot-rubric, fig.cap = "Distribution of students' scores across the grading rubric criteria. Each point is one student. Red lines indicate the mean score for all students per criterion."}
+include_graphics(here::here("analysis/figures/rubric_score_distribution.png"))
+```
+
 We graded the students’ final submissions using a rubric with criteria that covered content, the introduction, methods, result, and conclusion sections, and style.
-In Figure \@ref(fig:rubric-scores) we show the distribution and means of student scores for each criterion.
+In Figure \@ref(fig:show-plot-rubric) we show the distribution and means of student scores for each criterion.
 The two criteria showing the highest mean score are “Style: use commas and apostrophes correctly, and spell consistently”, and “Intro: has clear statement of the purpose of the report”.
@@
 The instructor will also benefit from a high tolerance for helping students to solve coding problems.
-To mitigate this in the future we will add a step of student peer review to give students an opportunity to get feedback and assistance from each other more formally.
+To mitigate this in the future we will add a step of student peer review to distribute the feedback task beyond the instructor and give students an opporutnity to get assistance from each other more formally.
 
@@
 Our main finding is that replication assignments are valued and in common use throughout the social sciences, and that they can be effective in teaching archaeology.
-Specifically, we found it possible to conduct a small scale replication assignment as part of an upper level undergraduate class.
-Student feedback was positive
+Specifically, we found it possible to conduct a small scale replication assignment as part of an upper level undergraduate archaeology class.
+Student feedback indicated that it was a valuable new experience for them, and for the discipline, even if they could not see themselves doing it again.
+We found that although this was a new and unconventional assignment, these elements did not have a negative effect on students' grades.
+Although our study is limited by its small size, when considered with the numerous other reports of replication assignments in other fields, we believe this approach will work in many types of archaeology classes.
+Replication assignments have an important role in closing the gap between the ideals of archaeological science and preparing students to tackle the practical challenges of doing archaeological science transparently and reproducibly.
 
-What are our main findings?
-
-What are the limitations of our study?
-Small sample size might affect statistical power, feedback survey as an assessment method might be subjective (comparison with grade ), control conditions: other factors that might have an impact on the replication paper
-
-What recommendations can we make to other archaeology instructors?
-Learning motivation, understanding of statistics and principles behind graphs with some exercises
-
-What will we do differently in the future?
+To make it easier to conduct replication assignments with archaeology students in the future, we recommend instructors share their syllabi and assignment instructions in trustworthy repositories such as the Open Science Framework (https://osf.io/) or Dataverse (https://dataverse.harvard.edu/).
+Currently it is hard to find examples and a more systematic and open way of sharing might reduce preparation time for instructors [cf.
+@hoffler2017replicationwiki].
+A second future direction in teaching replication is for archaeologists to share information about the software tools they use to make reproducible research easier.
+This information can be useful to guide instructors on what to teach students as part of their methods and software training [@janz2016bringing].
+In our review above we noted that teaching the use of tools like R, Markdown, Git and GitHub has already been embraced in many fields as core elements of graduate programs.
+Archaeology programs must place a greater emphasis on giving students skills to use tools that enable transparent and reproducible research.
 
 ## Acknowledgements
+
+Thanks to the students of ARCHY 483 in Spring 2019 for participating in the assignment.
 
@@
 <div id="refs"></div>
-
-Nosek, B. A., Alter, G., Banks, G. C., Borsboom, D., Bowman, S. D., Breckler, S. J., ... & Contestabile, M. (2015). Promoting an open research culture. Science, 348(6242), 1422-1425.
-
-Cliangirig Order: Replication arid Induction in Scientific Practice. BY H. M.
-COLLINS. London, Beverly Hills, and New Delhi: Sage Publications, 1985.
-Pp. viii -+ 187.
-
-Marwick, B. (2017). Computational reproducibility in archaeological research: basic principles and a case study of their implementation. Journal of Archaeological Method and Theory, 24(2), 424-450.
-
-Xie, Y., Allaire, J. J., & Grolemund, G. (2018). R markdown: The definitive guide. CRC Press.
-
-@Manual{,
-  title        = {R: A Language and Environment for Statistical
-                  Computing},
-  author       = {{R Core Team}},
-  organization = {R Foundation for Statistical Computing},
-  address      = {Vienna, Austria},
-  year         = YEAR,
-  url          = {https://www.R-project.org}
-}
-where YEAR is
 

### 2019-06-20 analysis/paper/plot-feedback-survey.R

@@ -1,4 +1,6 @@
 
+
+## ---- prepare-the-feedback-data
 library(tidyverse)
 feedback <- read_csv(here::here("analysis/data/raw_data/Replication report feedback Survey Student Analysis Report.csv"))
 
@@ -7,12 +9,12 @@ feedback <-
   feedback %>%
   rename_all(list(~str_squish(str_remove(., "\\d*:"))))
 
-# --- extract-yes-no-questions ---
+# extract-yes-no-questions ---
 feedback_yn <-
   feedback %>%
   select(6, 8)
 
-# --- extract-likert-scale-questions ---
+# extract-likert-scale-questions ---
 feedback_likert <-
   feedback %>%
   select(seq(10, 19, 2)) %>%
@@ -27,7 +29,9 @@ for(i in seq_along(feedback_likert)) {
   feedback_likert[,i] <- factor(feedback_likert[,i], levels=mylevels)
 }
 
-# --- plot-likert ---
+
+## ---- plot-the-feedback-data
+#  plot-likert ---
 require(likert)
 feedback_likert_out <- likert(feedback_likert)
 plot_l <- plot(feedback_likert_out,
@@ -35,7 +39,7 @@ plot_l <- plot(feedback_likert_out,
                legend.position = "top",
                base_size = 10)
 
-# --- plot-y-n
+# plot-y-n
 plot_y <-
 feedback_yn %>%
   gather(variable, value) %>%
@@ -53,20 +57,23 @@ feedback_yn %>%
   theme_minimal(base_size = 10) +
   scale_fill_grey()
 
-# --- combine-plots
+# combine-plots
 library(cowplot)
+feedback_plots <-
 plot_grid(plot_l,
           plot_y,
           ncol =1,
           rel_heights = c(4, 1))
 
-ggsave('analysis/figures/feedback_likert_yn_plot.png',
+ggsave(plot = feedback_plots,
+       here::here('analysis/figures/feedback_likert_yn_plot.png'),
                   height = 8,
                   width = 12)
 
 
-# --- likert-cor
+# likert-cor
 library(corrr)
+feedback_likert_out_plot <-
 feedback_likert_out$results %>%
   gather(variable, value, -Item) %>%
   mutate(Item = str_wrap(Item, 20)) %>%
@@ -76,7 +83,8 @@ feedback_likert_out$results %>%
   rplot() +
   scale_size(range = c(5, 20))
 
-ggsave('analysis/figures/feedback_likert_corr.png',
[…]

### 2019-06-20 analysis/paper/plot-rubric-scores.R

@@ -1,11 +1,11 @@
 
-
+## ---- prepare-the-rubric-data
 library(tidyverse)
 library(ggbeeswarm)
 
 #' read in the data
 # what a mess
-grading_rubric <- readxl::read_excel("analysis/data/raw_data/grading-rubric.xlsx")
+grading_rubric <- readxl::read_excel(here::here("analysis/data/raw_data/grading-rubric.xlsx"))
 
 #' clean the data
 criteria <-
@@ -56,7 +56,8 @@ grading_rubric %>%
   gather(student, score, -criteria) %>%
   mutate(prop = map_dbl(score, clean_and_ratio_the_score))
 
-#' Plot the distribution of scores
+## ---- plot-the-rubric-data
+rubric_data_plot <-
 scores %>%
   mutate(criteria = str_wrap((criteria), 40)) %>%
   ggplot(aes(reorder(criteria, prop),
@@ -68,12 +69,13 @@ scores %>%
                shape="\U007C",
                size=15,
                colour="red") +
-  labs(y = "Proportion of full score of that criterion",
+  labs(y = "Proportion of full score of each criterion",
        x = "Criterion") +
   theme_minimal(base_size = 12) +
   coord_flip()
 
-ggsave('analysis/figures/rubric_score_distribution.png',
+ggsave(plot = rubric_data_plot,
+       here::here('analysis/figures/rubric_score_distribution.png'),
        height = 8,
        width = 8)
 

### 2019-06-20 README.Rmd
travis and docker
add binder

@@
 # Please put your title here to include it in the file below. 
-Title <- "Title of your paper goes here"
+Title <- "How to use replication assignments for teaching integrity in empirical archaeology"
 ```
 
-# replicationteachingarchaeology
+# Teaching replication in archaeology
+<!-- badges: start -->
+[![Launch Rstudio Binder](http://mybinder.org/badge.svg)](https://mybinder.org/v2/gh/benmarwick/replicationteachingarchaeology/master?urlpath=rstudio) 
+[![Travis-CI Build Status](https://travis-ci.org/benmarwick/replicationteachingarchaeology.svg?branch=master)](https://travis-ci.org/benmarwick/replicationteachingarchaeology)
+<!-- badges: end -->
 
@@
 
-> Authors, (YYYY). _`r Title`_. Name of journal/book <https://doi.org/xxx/xxx>
+> Marwick, B., L. Wang, R. Robinson, H. Loiselle (2019). _`r Title`_. Name of journal/book <https://doi.org/10.17605/OSF.IO/DBSW9>
 
@@
 
-> Authors, (YYYY). _`r Title`_. Name of journal/book, Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/xxx/xxx>
+> Authors, (YYYY). _`r Title`_. Name of journal/book, Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/10.17605/OSF.IO/DBSW9>
 
@@
 
-> Authors, (`r format(Sys.Date(), "%Y")`). _Compendium of R code and data for `r Title`_. Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/xxx/xxx>
+> Marwick, B., L.
+Wang, R.
+Robinson, H.
+Loiselle, (`r format(Sys.Date(), "%Y")`).
+_Compendium of R code and data for `r Title`_.
+Accessed `r format(Sys.Date(), "%d %b %Y")`.
+Online at <https://doi.org/10.17605/OSF.IO/DBSW9>
 

### 2019-06-20 README.Rmd
docker hub

@@
 [![Travis-CI Build Status](https://travis-ci.org/benmarwick/replicationteachingarchaeology.svg?branch=master)](https://travis-ci.org/benmarwick/replicationteachingarchaeology)
+[![ORCiD](https://img.shields.io/badge/ORCiD-0000--0001--7879--4531-green.svg)](http://orcid.org/0000-0001-7879-4531)
+
 <!-- badges: end -->
@@
 
-> Authors, (YYYY). _`r Title`_. Name of journal/book, Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/10.17605/OSF.IO/DBSW9>
+> Authors, (2019). _`r Title`_. Name of journal/book, Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/10.17605/OSF.IO/DBSW9>
 
@@
 Loiselle, (`r format(Sys.Date(), "%Y")`).
-_Compendium of R code and data for `r Title`_.
+_Compendium of R code and data for "`r Title`"_.
 Accessed `r format(Sys.Date(), "%d %b %Y")`.
@@
 
-You can download the compendium as a zip from from this URL: </archive/master.zip>
+You can download the compendium as a zip from from this URL: [master.zip](/archive/master.zip)
 
-Or you can install this compendium as an R package, replicationteachingarchaeology, from GitHub with:
+Or you can install this compendium as an R package, teachingreplicationinarchaeology, from GitHub with:
+
 ### Licenses

### 2019-06-20 README.Rmd
typo

@@
 [![Launch Rstudio Binder](http://mybinder.org/badge.svg)](https://mybinder.org/v2/gh/benmarwick/replicationteachingarchaeology/master?urlpath=rstudio) 
-[![Travis-CI Build Status](https://travis-ci.org/benmarwick/replicationteachingarchaeology.svg?branch=master)](https://travis-ci.org/benmarwick/replicationteachingarchaeology)
+[![Travis-CI Build Status](https://travis-ci.org/benmarwick/teaching-replication-in-archaeology.svg?branch=master)](https://travis-ci.org/benmarwickteaching-replication-in-archaeology)
 [![ORCiD](https://img.shields.io/badge/ORCiD-0000--0001--7879--4531-green.svg)](http://orcid.org/0000-0001-7879-4531)

### 2019-06-20 analysis/paper/paper.Rmd
waiting for co-author edits

@@
 abstract: |
-  Text of abstract
-keywords: |
-  keyword 1; keyword 2; keyword 3
-highlights: |
-  These are the highlights. 
+  The value of new archaeological knowledge is strongly determined by how credible it is, and a key measure of scientific credibility is how replicable new results are.
+However, few archaeologists learn the skills necessary to conduct replication as part of their training.
+This means there is a gap between the ideals of archaeological science, and the skills we teach future researchers.
+Here we argue for replications as a core type of class assignment in archaeology courses to close this gap and establish a culture of replication and reproducibility.
+We review replication assignments in other fields, and describe how to implement a replication assignment suitable for many types of archaeology programs.
+We describe our experience with replication in an upper level undergraduate class on stone artefact analysis.
+Replication assignments can help archaeology programs give students skills that enable transparent and reproducible research.
 ---
@@
 
-# get text from google doc into Rmd
+# get text from google doc into Rmd, make sure we are in the target directory 
 download_rmd(file = "paper",  # do not include the .Rmd 

### 2019-06-21 analysis/paper/paper.Rmd
add edits from Ryan

@@
 
-To enable re-use of our materials and improve reproducibility and transparency according to the principles outlined in @marwick2017open, we include all our assingment materials, as well as the entire R code used for all the analysis and visualizations contained in this paper, in our compendium at http://doi.org/10.17605/OSF.IO/DBSW9.
+To enable re-use of our materials and improve reproducibility and transparency according to the principles outlined in @marwick2017open, we include all our assignment materials, as well as the entire R code used for all the analysis and visualizations contained in this paper, in our compendium at http://doi.org/10.17605/OSF.IO/DBSW9.
 Also in this version-controlled compendium are the raw data for the analyses reported here.
 The figures and results presented here can be independently reproduced with the code and data in this repository.
-In our compendium our code is released under the MIT licence, our data as CC-0, and our figures and assingment materials as CC-BY, to enable maximum re-use [for more details, see @Marwick2017].
+In our compendium our code is released under the MIT licence, our data as CC-0, and our figures and assignment materials as CC-BY, to enable maximum re-use [for more details, see @Marwick2017].
 
@@
 Some of the earliest discussions of replication in university curricula appear in economics and psychology [@hoffler2013teaching; @standing2014using].
-@Ball_Medeiros_2012 describe their TIER (teaching integrity in empirical research) protocol for undergraduate economics students at Haverford College.
+@Ball_Medeiros_2012 describe their TIER (Teaching Integrity in Empirical Research) protocol for undergraduate economics students at Haverford College.
 This is intended to ensure that a student's work is replicable by the instructors.
@@
 The instructor will also benefit from a high tolerance for helping students to solve coding problems.
-To mitigate this in the future we will add a step of student peer review to distribute the feedback task beyond the instructor and give students an opporutnity to get assistance from each other more formally.
+To mitigate this in the future we will add a step of student peer review to distribute the feedback task beyond the instructor and give students an opportunity to get assistance from each other more formally.
 

### 2019-06-21 analysis/paper/paper.Rmd
add citation to Spearman

@@
 
-```{r show-plot-feedback-correlations, fig.cap = "Correlations among feedback items with Likert scale responses.
+(ref:correlation-caption) Correlations among feedback items with Likert scale responses.
 The size of the dot indicates the magnitude of the correlation, and the colour indicates the direction (red is negative, blue is positive).
-Correlations were computed using Spearman's method."}
+Correlations were computed using Spearman's [-@spearman1904proof] method.
+
+```{r show-plot-feedback-correlations, fig.cap = "(ref:correlation-caption)"}
 include_graphics(here::here("analysis/figures/feedback_likert_corr.png"))

### 2019-06-23 analysis/paper/paper.Rmd
add edits from Hope

@@
 In this paper we propose a new type of assignment for the archaeology classroom, the replication report, to better align the practice of teaching archaeology with the transparency and openness ideals of science [@nosek2015promoting].
-The replication report assignment involves three key steps: 1) students analysing a published report to determine what are the main claims made by the authors of that report, 2) students obtaining the data used by the authors, and 3) analysing that data to determine if one or more of the authors’ claims are reliable.
+The replication report assignment involves three key steps: 1) students analysing a published report to determine the main claims made by the authors of that report, 2) students obtaining the data used by the authors, and 3) analysing that data to determine if one or more of the authors’ claims are reliable.
 
-We describe how to implement a replication report assignment suitable for upper level undergraduates and graduate students in archaeology.
-Our experience is based on an upper level archaeology class on stone artefact analysis taught during the Spring quarter of 2019 at the University of Washington.
+We describe how to implement a replication report assignment suitable for upper-level undergraduates and graduate students in archaeology.
+Our experience is based on an upper-level archaeology class on stone artefact analysis taught during the Spring quarter of 2019 at the University of Washington.
 The class format includes a weekly cycle of lecture, discussion seminar, and hands-on laboratory activities.
 The assignments include seminar notes, lecture quizzes, laboratory worksheets, and two longer empirical reports.
-For the term that we report here, the class had 16 students, and one graduate student teaching assistant.
+For the term that we report here, the class had 16 students and one graduate student teaching assistant.
 This is a typical size for this class, and similar to the usual size of upper-level laboratory classes in the archaeology program at the University of Washington.
-Our students are mostly in social science and humanities majors with diverse levels of statistical knowledge.
+Our students are mostly in social science and humanities majors with varying levels of statistical competence.
 Here we survey the literature on similar types of assignments in other fields to identify common elements that other fields have identified as important principles and skills.
@@
 The figures and results presented here can be independently reproduced with the code and data in this repository.
-In our compendium our code is released under the MIT licence, our data as CC-0, and our figures and assignment materials as CC-BY, to enable maximum re-use [for more details, see @Marwick2017].
+In our compendium our code is released under the MIT license, our data as CC-0, and our figures and assignment materials as CC-BY, to enable maximum re-use [for more details, see @Marwick2017].
 
@@
 
-@barba2018terminologies points out that there is confusion and conflicting uses of the terms "reproducibility" and "replication" in recent years.
-In her survey of relevant literature from many disciplines, Barba finds that some fields make no distinction between "reproducibility" and "replication", and among fields that do recognise a distinction between the two, the meanings are sometimes directly swapped from one discipline to another.
-Here we follow what Barba has identified as the most common, long-established and highly cited definitions of these terms, and these are also the same as recently recommended by the National Academies of Sciences, Engineering, and Medicine (2019).
+@barba2018terminologies points out that although there has been prolific discussion of the terms "reproducibility" and "replication" in many disciplines in recent years, confusion and conflicting uses are widespread.
+In her survey of relevant literature, Barba finds that some fields make no distinction between "reproducibility" and "replication", and among fields that do recognise a distinction between the two, the meanings are sometimes directly inverted.
+Here we follow what Barba has identified as the most common, long-established and highly cited definitions of these terms, as also recently recommended by the National Academies of Sciences, Engineering, and Medicine (2019).
 Reproducibility is the ability to obtain results by using the same data, code, and procedures provided by the original authors [@Marwick2017].
@@
 Replication assignments across different fields may not strictly fit into the above definition of replication because they do not always involve a completely new study.
-We consider that if a study departs from any of the original materials e.g.
+Nevertheless, we consider that if a study departs from any of the original materials, e.g.
 new data with previously published code, or new code with previously published data, then it is broadly within the definition of replication.
@@
 
-Students in Stanford University’s graduate course ‘Advanced Topics in Networking’ are given a replication assignment in which they are asked to replicating 'classic' computer networking experiments [@yan2017learning].
+Students in Stanford University’s graduate course ‘Advanced Topics in Networking’ are given a replication assignment in which they are asked to replicate 'classic' computer networking experiments [@yan2017learning].
 Students work in pairs and receive modest instructor support.
@@
 
-For the first step we supplied students with a list of journal articles that included raw data and R code either in supplemental files or deposited on open data repositories.
+For the first step, we supplied students with a list of journal articles that included raw data and R code either in supplemental files or deposited on open data repositories.
 This list is updated regularly, but is not exhaustive, and is currently online at https://github.com/benmarwick/ctv-archaeology.
@@
 Some authors include their data as a file in the supplementary information attached to the article, while others deposit their files on an open data repository such as osf.io or figshare.com, and then cite the DOI to the files in their article.
-Where the data files were nested in several layers of folders, some students struggled to find them.
+When the data files were nested in several layers of folders, some students struggled to find them.
 
@@
 High scores for the grammar criterion are expected because these reflect basic writing skills required for many undergraduate-level courses.
-Students are expected to have learned these in lower level classes before taking this class.
+Students are expected to have learned these in lower-level classes before taking this class.
 The high scores relating to the introduction section may reflect the effectiveness of the scaffolding steps that focused students on the specific purpose of the assignment.
@@
 This might result from insufficient prior training in searching for scholarly publications, suggesting that although this is also a skill that should have been acquired before taking this class, many students remain weak at this task.
-A low mean is also evident for "Intro: has names, locations, and basic chronology of sites", because some students neglected to supply these archaeological details.
+A low mean is also evident for "Intro: has names, locations, and basic chronology of sites," because some students neglected to supply these archaeological details.
 Future use of this assignment will incorporate these low-scoring criteria into the scaffolding steps to emphasize their importance to students and give an opportunity for early feedback to students.
@@
 The criteria most relevant to the replication component of the assignment, in order from highest mean score to lowest, are "Content: submission includes Rmd file, Data file, and Word file",  "Conclusion: state whether the author’s claims appear to be robust, unreliable, etc", "Results: includes 1-2 original plots & description of these", and "Methods: identify the specific results you will replicate".
-This suggests that we could help students to develop a better skills in narrating their process (writing about methods), and describing and interpreting their data visualizations.
+This suggests that we could help students to develop better skills in narrating their process (writing about methods), and describing and interpreting their data visualizations.
 In the future we may include more fundamental exercises focusing on these tasks in the scaffolding steps.
@@
 Our main finding is that replication assignments are valued and in common use throughout the social sciences, and that they can be effective in teaching archaeology.
-Specifically, we found it possible to conduct a small scale replication assignment as part of an upper level undergraduate archaeology class.
+Specifically, we found it possible to conduct a small scale replication assignment as part of an upper-level undergraduate archaeology class.
 Student feedback indicated that it was a valuable new experience for them, and for the discipline, even if they could not see themselves doing it again.
@@
 To make it easier to conduct replication assignments with archaeology students in the future, we recommend instructors share their syllabi and assignment instructions in trustworthy repositories such as the Open Science Framework (https://osf.io/) or Dataverse (https://dataverse.harvard.edu/).
-Currently it is hard to find examples and a more systematic and open way of sharing might reduce preparation time for instructors [cf.
+Currently, it is hard to find examples and a more systematic and open way of sharing might reduce preparation time for instructors [cf.
 @hoffler2017replicationwiki].

### 2019-06-23 analysis/paper/paper.Rmd
add Wessa

@@
 The longer term practical benefits include cultivating a reproducibility routine for students to develop a natural habit of organising their code and data for future work so another person can use it to reproduce their results.
-Benefits also include developing professionalism among students: by working through the steps of an analysis students gain an understanding of what kinds of decisions in all steps of an analysis are acceptable (Janz 2018).
+Benefits also include developing professionalism among students: by working through the steps of an analysis students gain an understanding of what kinds of decisions in all steps of an analysis are acceptable [@janz2016bringing].
 Although the small scale of our assignment did not offer the potential for students to publish new findings from replication, we anticipate this may be a benefit for archaeology students participating in more extensive replication assignments.
@@
 The instructor will also benefit from a high tolerance for helping students to solve coding problems.
-To mitigate this in the future we will add a step of student peer review to distribute the feedback task beyond the instructor and give students an opportunity to get assistance from each other more formally.
+To mitigate this in the future we will add a step of student peer review [@wessa2009reproducible] to distribute the feedback task beyond the instructor and give students an opportunity to get assistance from each other more formally.
 

### 2019-06-23 README.Rmd
update readme
Update README.Rmd

--- 2019-06-20 README.Rmd
@@
 [![Launch Rstudio Binder](http://mybinder.org/badge.svg)](https://mybinder.org/v2/gh/benmarwick/replicationteachingarchaeology/master?urlpath=rstudio) 
-[![Travis-CI Build Status](https://travis-ci.org/benmarwick/replicationteachingarchaeology.svg?branch=master)](https://travis-ci.org/benmarwick/replicationteachingarchaeology)
+[![Travis-CI Build Status](https://travis-ci.org/benmarwick/teaching-replication-in-archaeology.svg?branch=master)](https://travis-ci.org/benmarwick/teaching-replication-in-archaeology)
 [![ORCiD](https://img.shields.io/badge/ORCiD-0000--0001--7879--4531-green.svg)](http://orcid.org/0000-0001-7879-4531)
@@
 
-> Authors, (2019). _`r Title`_. Name of journal/book, Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/10.17605/OSF.IO/DBSW9>
+> Marwick, B., L. Wang, R. Robinson, H. Loiselle , (2019). _`r Title`_. SocArXiv, Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://osf.io/preprints/socarxiv/tsxbv>
 

### 2019-08-13 analysis/paper/paper.Rmd
working on peer revierws: apply SAA citation style

@@
 bibliography: references.bib
-csl: "../templates/journal-of-archaeological-science.csl" # Insert path for the bib-style
+csl: "../templates/society-for-american-archaeology.csl" # Insert path for the bib-style
 abstract: |

### 2019-08-15 README.Rmd
finished dealing with reviewers' comments on the ms.

@@
 
-### How to download or install
+### Overview of contents
+
+The **analysis** directory contains:  
+- **paper** has our R Markdown document, paper.Rmd, that contains text and code of our paper.
+It also has a rendered version, paper.docx, suitable for reading (the code is replaced by figures and tables in this file)
+- **data** has our raw data files    
+- **figures** has our plots and other illustrations
+
+### How to run, download or install
+
+The simplest way to explore the text, code and data is to click on [binder](https://mybinder.org/v2/gh/benmarwick/replicationteachingarchaeology/master?urlpath=rstudio) to open an instance of RStudio in your browser, which will have the compendium files ready to work with.
 
@@
 Or you can install this compendium as an R package, teachingreplicationinarchaeology, from GitHub with:
+
+```
+remotes::install_github("benmarwick/teachingreplicationinarchaeology")
+```
 

### 2019-08-15 analysis/paper/paper.Rmd
finished dealing with reviewers' comments on the ms.

@@
 ---
-title: "How to use replication assignments for teaching integrity in empirical archaeology"
+title             : "How to use replication assignments for teaching integrity in empirical archaeology"
+
 author:
-  - Ben Marwick, bmarwick@uw.edu
+  -  Ben Marwick
   -  Liying Wang
@@
   -  Hope Loiselle
-date: "`r format(Sys.time(), '%d %B, %Y')`"
-output: 
-    bookdown::word_document2:
-      fig_caption: yes
-      reference_docx: "../templates/template.docx" # Insert path for the DOCX file
-bibliography: references.bib
-csl: "../templates/society-for-american-archaeology.csl" # Insert path for the bib-style
+
 abstract: |
@@
 Replication assignments can help archaeology programs give students skills that enable transparent and reproducible research.
+
+bibliography      : "references.bib"
+output: 
+    bookdown::word_document2:
+      fig_caption: yes
+      reference_docx: "../templates/template.docx" # Insert path for the DOCX file
 ---
@@
 In this paper we propose a new type of assignment for the archaeology classroom, the replication report, to better align the practice of teaching archaeology with the transparency and openness ideals of science [@nosek2015promoting].
-The replication report assignment involves three key steps: 1) students analysing a published report to determine the main claims made by the authors of that report, 2) students obtaining the data used by the authors, and 3) analysing that data to determine if one or more of the authors’ claims are reliable.
+The replication report assignment involves three four steps: 1) students analysing a published report to determine the main claims made by the authors of that report, 2) students obtaining the data used by the authors, 3) analysing that data to help determine if one or more of the authors’ claims are reliable, and 4) submitting a research compendium that documents the students' work in a reproducible format that includes the code and data used in the assignment.
 
@@
 In her survey of relevant literature, Barba finds that some fields make no distinction between "reproducibility" and "replication", and among fields that do recognise a distinction between the two, the meanings are sometimes directly inverted.
-Here we follow what Barba has identified as the most common, long-established and highly cited definitions of these terms, as also recently recommended by the National Academies of Sciences, Engineering, and Medicine (2019).
+Here we follow what Barba has identified as the most common, long-established and highly cited definitions of these terms, as also recently recommended by the National Academies of Sciences, Engineering, and Medicine [-@national2019reproducibility].
 Reproducibility is the ability to obtain results by using the same data, code, and procedures provided by the original authors [@Marwick2017].
@@
 Students report a high rate of engaging in open science practices after taking the class, and 80% of the participants said that they believe the open science techniques will improve their future research as professionals [@toelch2018digital].
-Millman et al (2018) describe a similar course at Berkeley that teaches students how to use open science tools to complete a capstone replication assignment on neuroscience topics.
+@Millman_Brett_Barnowski_Poline_2018 describe a similar course at Berkeley that teaches students how to use open science tools to complete a capstone replication assignment on neuroscience topics.
 
@@
 @roettger2018towards] .
-Common elements include group work, use of open science software and services to make the replication results openly accessible to anyone, and a scaffolded, stepwise approach to the task to ensure that students receive instructor support at multiple stages in the assignment.
-To the best of our knowledge replication assignments are not common in archaeology programs.
+Common elements include group work, use of open source software and services to make the replication results openly accessible to anyone, and a scaffolded, stepwise approach to the task to ensure that students receive instructor support at multiple stages in the assignment.
+To the best of our knowledge replication assignments are not common in archaeology programs, although the tools and data structures are generally similar to other social sciences.
 We posted a message to the Society of American Archaeology Teaching Archaeology Interest Group e-community on 27 May 2019 to ask for examples of replication assignments used in teaching archaeology, and received no replies from anyone teaching with replication.
+More broadly in archaeology replication and reproducibility has received limited, but growing, attention.
+Elsewhere we have documented recent rapid increases in the number of publications that include code and data to enable readers to reproduce the published results [@Marwick_Schmidt_2019]
 
@@
 Submissions for each step were graded as complete/incomplete, with feedback provided individually via the Canvas learning management system, and collectively during class meetings.
-Our course had no prerequisites, so we assumed no prior knowledge of the R programming language among the students, and were prepared to teach them as complete novices.
+Our course had no prerequisites, so we assumed no prior knowledge of the free and open source R programming language among the students, and were prepared to teach them as complete novices.
 We chose R [@R_core_team] because it is widely used by archaeologists [@Schmidt2019], and also commonly taught in undergraduate classes in social sciences and statistics [@baumer2014r; @ccetinkaya2018infrastructure; @dvorak2019efficient].
@@
 An R Markdown document is written in markdown (a simple plain text format) and contains chunks of embedded R code [@xie2018r].
-The document can be easily converted into many standard formats, such as Microsoft Word, PDF and HTML.
+The document can be easily converted into many standard formats, such as Microsoft Word, PDF and HTML, we give more detail about this in @Marwick2017.
 We prepared an R Markdown template file with some basic headings (following the IMRaD or Introduction-Method-Results-and-Discussion format) and empty code chunks to provide guidance to the students on how many code chunks were expected, and where in the document they should appear.
@@
 Microsoft Word document that is produced when they knit the R Markdown file).
+The students submitted these materials to Canvas for grading.
+We did not make the student work public, unlike some of examples described above that deposit student work in public on the Open Science Framework.
 Our expectation was that we could reproduce any student’s results by running their submitted R Markdown document with the raw data file to produce the Word document they submitted.
@@
 As a consequence, we were prepared to intervene to guide their selection of a paper that we could be sure they could successfully replicate, given the time available.
+The target articles used by this class were @Marwick_Clarkson_O_Connor_Collins_2016, @Bicho2020, and @Marwick_2013.
 
@@
 
-```{r show-plot-feedback, fig.cap = "Results of the anonymous feedback survey on the replication assignment"}
-include_graphics(here::here("analysis/figures/feedback_likert_yn_plot.png"))
-```
-
 Thirteen out of sixteen students completed an anonymous feedback survey (Figure \@ref(fig:show-plot-feedback)).
@@
 Most, but not all, students agreed that the replication assignment helped them to learn more effectively than reading a paper to write a traditional paper.
-
-(ref:correlation-caption) Correlations among feedback items with Likert scale responses.
-The size of the dot indicates the magnitude of the correlation, and the colour indicates the direction (red is negative, blue is positive).
-Correlations were computed using Spearman's [-@spearman1904proof] method.
-
-```{r show-plot-feedback-correlations, fig.cap = "(ref:correlation-caption)"}
-include_graphics(here::here("analysis/figures/feedback_likert_corr.png"))
-```
 
@@
 
-```
-
-```{r show-plot-rubric, fig.cap = "Distribution of students' scores across the grading rubric criteria. Each point is one student. Red lines indicate the mean score for all students per criterion."}
-include_graphics(here::here("analysis/figures/rubric_score_distribution.png"))
 ```
@@
 In addition to time, the instructor needs to have a high skill level in quantitative methods to guide students in their engagement with the literature.
-The instructor will also benefit from a high tolerance for helping students to solve coding problems.
+The instructor will also benefit from a high tolerance for helping students to solve coding problems, and having a teaching assistent with a suitable background and similar qualities.
 To mitigate this in the future we will add a step of student peer review [@wessa2009reproducible] to distribute the feedback task beyond the instructor and give students an opportunity to get assistance from each other more formally.
@@
 
-<!-- The following line inserts a page break when the output is MS Word. For page breaks in PDF, use \newpage on its own line.  -->
-##### pagebreak
-
 # References 
@@
 
-##### pagebreak
+```{r show-plot-feedback, fig.cap = "Results of the anonymous feedback survey on the replication assignment", fig.align='center'}
+include_graphics(here::here("analysis/figures/feedback_likert_yn_plot.png"))
+```
+
+(ref:correlation-caption) Correlations among feedback items with Likert scale responses.
+The size of the dot indicates the magnitude of the correlation, and the colour indicates the direction (red is negative, blue is positive).
+Correlations were computed using Spearman's [-@spearman1904proof] method.
+
+```{r show-plot-feedback-correlations, fig.cap = "(ref:correlation-caption)", fig.align='center'}
+include_graphics(here::here("analysis/figures/feedback_likert_corr.png"))
+```
+
+```{r show-plot-rubric, fig.cap = "Distribution of students' scores across the grading rubric criteria.
+Each point is one student.
+Red lines indicate the mean score for all students per criterion.", fig.align='center'}
+include_graphics(here::here("analysis/figures/rubric_score_distribution.png"))
+```
 

### 2019-08-15 analysis/paper/plot-feedback-survey.R

@@ -36,8 +36,11 @@ require(likert)
 feedback_likert_out <- likert(feedback_likert)
 plot_l <- plot(feedback_likert_out,
                wrap = 30,
-               legend.position = "top",
-               base_size = 10)
+               text.size = 2,
+               legend.position = "top") +
+  theme(text=element_text(size=4),
+        axis.text=element_text(size=4),
+        legend.text = element_text(size = 5.5))
 
 # plot-y-n
 plot_y <-
@@ -54,7 +57,7 @@ feedback_yn %>%
   labs(x = "",
        y = "Number of responses") +
   coord_flip() +
-  theme_minimal(base_size = 10) +
+  theme_minimal(base_size = 6) +
   scale_fill_grey()
 
 # combine-plots
@@ -67,8 +70,8 @@ plot_grid(plot_l,
 
 ggsave(plot = feedback_plots,
        here::here('analysis/figures/feedback_likert_yn_plot.png'),
-                  height = 8,
-                  width = 12)
+                  width = 5.75,
+       dpi = 300)
 
 
 # likert-cor
@@ -80,13 +83,16 @@ feedback_likert_out$results %>%
   spread(Item, value) %>%
   select(-1) %>%
   correlate(method = "spearman") %>%
+  shave(upper = FALSE) %>%
   rplot() +
-  scale_size(range = c(5, 20))
+  scale_size(range = c(5, 20)) +
+  theme(axis.text=element_text(size=6))
 
 ggsave(plot = feedback_likert_out_plot,
        here::here('analysis/figures/feedback_likert_corr.png'),
-       height = 8,
-       width = 10)
+       width = 5.75,
+       h = 5.75,
+       dpi = 300)
 
 
 

### 2019-08-15 analysis/paper/plot-rubric-scores.R

@@ -71,13 +71,12 @@ scores %>%
                colour="red") +
   labs(y = "Proportion of full score of each criterion",
        x = "Criterion") +
-  theme_minimal(base_size = 12) +
+  theme_minimal(base_size = 8) +
   coord_flip()
 
 ggsave(plot = rubric_data_plot,
        here::here('analysis/figures/rubric_score_distribution.png'),
-       height = 8,
-       width = 8)
+       width = 5.75)
 
 
 

### 2019-08-15 analysis/paper/paper.Rmd
send the ms. to co-authors for final approval after peer reviews
mention that we have examples of student submissions on OSF

@@
 The figures and results presented here can be independently reproduced with the code and data in this repository.
-In our compendium our code is released under the MIT license, our data as CC-0, and our figures and assignment materials as CC-BY, to enable maximum re-use [for more details, see @Marwick2017].
+In our compendium our code is released under the MIT license, our data as CC-0, and our figures, and assignment instructions and grading rubric as CC-BY, to enable maximum re-use [for more details, see @Marwick2017].
 
@@
 The students submitted these materials to Canvas for grading.
-We did not make the student work public, unlike some of examples described above that deposit student work in public on the Open Science Framework.
+Two complete student submissions are available for inspection in our compendium at http://doi.org/10.17605/OSF.IO/DBSW9.
+We did not make all the student work public, unlike some of examples described above that deposit student work in public on the Open Science Framework.
 Our expectation was that we could reproduce any student’s results by running their submitted R Markdown document with the raw data file to produce the Word document they submitted.
@@
 
-Thanks to the students of ARCHY 483 in Spring 2019 for participating in the assignment.
+Thanks to the students of ARCHY 483 in Spring 2019 for participating in the assignment. Thanks to the peer reviewers for their detailed feedback and suggestions for improvement.
 

### 2019-08-15 README.Rmd
improve the readme to make it more clear what this is, and what to do with it

--- 2019-06-23 README.Rmd
@@
 [![Travis-CI Build Status](https://travis-ci.org/benmarwick/teaching-replication-in-archaeology.svg?branch=master)](https://travis-ci.org/benmarwick/teaching-replication-in-archaeology)
-[![ORCiD](https://img.shields.io/badge/ORCiD-0000--0001--7879--4531-green.svg)](http://orcid.org/0000-0001-7879-4531)
 
@@
 
-> Marwick, B., L. Wang, R. Robinson, H. Loiselle (2019). _`r Title`_. Name of journal/book <https://doi.org/10.17605/OSF.IO/DBSW9>
+> Marwick, B.
+[![](https://orcid.org/sites/default/files/images/orcid_16x16.png)](https://orcid.org/0000-0001-7879-4531), L.
+Wang [![](https://orcid.org/sites/default/files/images/orcid_16x16.png)](https://orcid.org/0000-0001-9060-2125), R.
+Robinson, H.
+Loiselle (2019).
+_`r Title`_.
+Submitted to _Advances in Archaeological Practice_ <https://doi.org/10.17605/OSF.IO/DBSW9>
 
@@
 
-### How to download or install
+### Overview of contents
 
-You can download the compendium as a zip from from this URL: [master.zip](/archive/master.zip)
+## Contents
 
-Or you can install this compendium as an R package, teachingreplicationinarchaeology, from GitHub with:
+The **analysis** directory contains:
+
+- [:file_folder: paper](/analysis/paper): R Markdown source document for manuscript.
+Includes code to reproduce the figures and tables generated by the analysis.
+It also has a rendered version, `paper.docx`, suitable for reading (the code is replaced by figures and tables in this file)
+- [:file_folder: data](/analysis/data): Data used in the analysis.  
+- [:file_folder: figures](/analysis/figures): Plots and other illustrations
+
+### How to run in your broswer or download and run locally
+
+The simplest way to explore the text, code and data is to click on [binder](https://mybinder.org/v2/gh/benmarwick/replicationteachingarchaeology/master?urlpath=rstudio) to open an instance of RStudio in your browser, which will have the compendium files ready to work with.
+Binder uses rocker-project.org Docker images to ensure a consistent and reproducible computational environment.
+These Docker images can also be used locally.
+
+You can download the compendium as a zip from from this URL: [master.zip](/archive/master.zip).
+After unzipping, open the `Proj` file in RStudio, and run `devtools::install()` to ensure you have the packages this analysis depends on (also listed in the [DESCRIPTION](/DESCRIPTION) file).
+Then open `paper.Rmd` and knit to produce the `paper.docx`.
 

### 2019-08-16 README.Rmd
tweaks to readme
add Ryan's ORCID
add more orcids :)

@@
 Wang [![](https://orcid.org/sites/default/files/images/orcid_16x16.png)](https://orcid.org/0000-0001-9060-2125), R.
-Robinson, H.
-Loiselle (2019).
+Robinson [![](https://orcid.org/sites/default/files/images/orcid_16x16.png)](https://orcid.org/0000-0001-8029-937X), H.
+Loiselle [![](https://orcid.org/sites/default/files/images/orcid_16x16.png)](https://orcid.org/0000-0002-6197-4752) (2019).
 _`r Title`_.
@@
 
-### Overview of contents
-
 ## Contents
@@
 
-### How to run in your broswer or download and run locally
+## How to run in your broswer or download and run locally
 

### 2019-08-16 analysis/paper/paper.Rmd
improve the readme to make it more clear what this is, and what to do with it
Add Hope's commas 👓

@@
 However, few archaeologists learn the skills necessary to conduct replication as part of their training.
-This means there is a gap between the ideals of archaeological science, and the skills we teach future researchers.
-Here we argue for replications as a core type of class assignment in archaeology courses to close this gap and establish a culture of replication and reproducibility.
+This means there is a gap between the ideals of archaeological science and the skills we teach future researchers.
+Here, we argue for replications as a core type of class assignment in archaeology courses to close this gap and establish a culture of replication and reproducibility.
 We review replication assignments in other fields, and describe how to implement a replication assignment suitable for many types of archaeology programs.
-We describe our experience with replication in an upper level undergraduate class on stone artefact analysis.
+We describe our experience with replication in an upper-level undergraduate class on stone artefact analysis.
 Replication assignments can help archaeology programs give students skills that enable transparent and reproducible research.
@@
 In this paper we propose a new type of assignment for the archaeology classroom, the replication report, to better align the practice of teaching archaeology with the transparency and openness ideals of science [@nosek2015promoting].
-The replication report assignment involves three four steps: 1) students analysing a published report to determine the main claims made by the authors of that report, 2) students obtaining the data used by the authors, 3) analysing that data to help determine if one or more of the authors’ claims are reliable, and 4) submitting a research compendium that documents the students' work in a reproducible format that includes the code and data used in the assignment.
+The replication report assignment involves four steps: 1) students analysing a published report to determine the main claims made by the authors of that report, 2) students obtaining the data used by the authors, 3) analysing that data to help determine if one or more of the authors’ claims are reliable, and 4) submitting a research compendium that documents the students' work in a reproducible format including the code and data used in the assignment.
 
@@
 Our students are mostly in social science and humanities majors with varying levels of statistical competence.
-Here we survey the literature on similar types of assignments in other fields to identify common elements that other fields have identified as important principles and skills.
+Here, we survey the literature on similar types of assignments in other fields to identify common elements that other fields have identified as important principles and skills.
 We describe our assignment and discuss student feedback on our implementation.
@@
 The figures and results presented here can be independently reproduced with the code and data in this repository.
-In our compendium our code is released under the MIT license, our data as CC-0, and our figures, and assignment instructions and grading rubric as CC-BY, to enable maximum re-use [for more details, see @Marwick2017].
+In our compendium, our code is released under the MIT license, our data as CC-0, and our figures, and assignment instructions and grading rubric as CC-BY, to enable maximum re-use [for more details, see @Marwick2017].
 
@@
 @barba2018terminologies points out that although there has been prolific discussion of the terms "reproducibility" and "replication" in many disciplines in recent years, confusion and conflicting uses are widespread.
-In her survey of relevant literature, Barba finds that some fields make no distinction between "reproducibility" and "replication", and among fields that do recognise a distinction between the two, the meanings are sometimes directly inverted.
+In her survey of relevant literature, Barba finds that some fields make no distinction between "reproducibility" and "replication." Among fields that do recognise a distinction between the two, the meanings are sometimes directly inverted.
 Here we follow what Barba has identified as the most common, long-established and highly cited definitions of these terms, as also recently recommended by the National Academies of Sciences, Engineering, and Medicine [-@national2019reproducibility].
@@
 
-In the following section we briefly survey replication assignments described in other fields to survey the variety of forms this usually takes.
+In the following section, we briefly survey replication assignments described in other fields to survey the variety of forms this usually takes.
 Replication assignments across different fields may not strictly fit into the above definition of replication because they do not always involve a completely new study.
@@
 Common elements include group work, use of open source software and services to make the replication results openly accessible to anyone, and a scaffolded, stepwise approach to the task to ensure that students receive instructor support at multiple stages in the assignment.
-To the best of our knowledge replication assignments are not common in archaeology programs, although the tools and data structures are generally similar to other social sciences.
+To the best of our knowledge, replication assignments are not common in archaeology programs, although the tools and data structures are generally similar to other social sciences.
 We posted a message to the Society of American Archaeology Teaching Archaeology Interest Group e-community on 27 May 2019 to ask for examples of replication assignments used in teaching archaeology, and received no replies from anyone teaching with replication.
-More broadly in archaeology replication and reproducibility has received limited, but growing, attention.
-Elsewhere we have documented recent rapid increases in the number of publications that include code and data to enable readers to reproduce the published results [@Marwick_Schmidt_2019]
+More broadly in archaeology, replication and reproducibility has received limited, but growing, attention.
+Elsewhere, we have documented recent rapid increases in the number of publications that include code and data to enable readers to reproduce the published results [@Marwick_Schmidt_2019]
 
@@
 Our main finding is that replication assignments are valued and in common use throughout the social sciences, and that they can be effective in teaching archaeology.
-Specifically, we found it possible to conduct a small scale replication assignment as part of an upper-level undergraduate archaeology class.
+Specifically, we found it possible to conduct a small-scale replication assignment as part of an upper-level undergraduate archaeology class.
 Student feedback indicated that it was a valuable new experience for them, and for the discipline, even if they could not see themselves doing it again.
@@
 # what commit is this file at? 
-git2r::repository(here::here())
+if(git2r::in_repository(path = ".")) git2r::repository(here::here())
 ```

### 2019-08-17 README.Rmd
resubmit after peer reviews

@@
 - [:file_folder: figures](/analysis/figures): Plots and other illustrations
+- [:file_folder: figures](/analysis/supplementary-materials): Supplementary materials including the assignment instructions that we used with the students, and two completed assignments submitted by students in this class.
 

### 2019-08-17 analysis/paper/paper.Rmd
resubmit after peer reviews

@@
 More broadly in archaeology, replication and reproducibility has received limited, but growing, attention.
-Elsewhere, we have documented recent rapid increases in the number of publications that include code and data to enable readers to reproduce the published results [@Marwick_Schmidt_2019]
+Elsewhere, we have documented recent rapid increases in the number of publications that include code and data to enable readers to reproduce the published results [@Schmidt2019]
 

### 2019-08-17 analysis/supplementary-materials/assignment-instructions/template-for-archy-483-replication-report.Rmd
resubmit after peer reviews

---
title: "Spring 2019 ARCHY 483 Replication Report"
author: "My Name"
date: "`r Sys.Date()`"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE) # this ensures we can see your code in the output
```

## Introduction

## Methods

## Results

```{r read-in-the-data}

```

```{r tidy-the-data}

```

```{r plot-the-data}

```

## Conclusion

## References cited

<!-- don't delete the line below, it will count the words in your report. You will need to do a one-time install of the wordcountaddin package first by running this code in your console: source("https://install-github.me/benmarwick/wordcountaddin") #  -->
Word count: `r wordcountaddin::word_count()`

### 2019-08-17 analysis/supplementary-materials/submitted-assigments/Hope-Loiselle/Replication_Report_Lithics.Rmd
resubmit after peer reviews

---
title: "Replication_Report_Lithics"
output:
  word_document: default
  html_document: default
---
---
title: "Spring 2019 ARCHY 483 Replication Report"
author: "Hope Loiselle"
date: "`r Sys.Date()`"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      warning = FALSE, message = FALSE) # this ensures we can see your code in the output
```

## Introduction 
This report looks to substantiate the claim made by Marwick (2013) in the paper "Multiple Optima in Hoabinhian flaked stone artefact palaeoeconomics and palaeoecology at two archaeological sites in Northwest Thailand," that the major climate shift between the Pleistocene and the Holocene affected the technological behavior of people living at the sites of Ban Rai and Tham Lod.

This report uses data from two sites in Thailand: Ban Rai and Tham Lod. Ban Rai is a Holocene rockshelter site in a steep valley of the Shan mountain range, dating from about 10,000 BP to 6,000 BP. The site is located in semi-evergreen vegetation and bamboo. Tham Lod is also a rockshelter and dates to the Pleistocene, about 40,000 BP to 10,000 BP. The environment around Tham Lod consists of karst formations and steep, low hills, with semi-evergreen forest (Marwick 2013). Citkament et al. (2015) detail the types of tools that can be found at Tham Lod, including locally sourced cores.

## Methods
In order to substantiate the claims made by Marwick, data from Ban Rai and Tham Lod was analyzed to determine the median percent of dorsal cortex for each site and the mean proportion of no cortex for each site (following methods of measuring reduction in Marwick 2008b). To determine the median % dorsal cortex, a boxplot was created for each site. To calculate the mean proportion of no cortex found at the site, the data was first grouped by site, excavation layer/unit and the amount of dorsal cortex. Then the proportion of no-cortex to cortex was calculated within each excavation unit. The resulting proportions were graphed for each site using a boxplot.

## Results

```{r read-in-the-data}
suppressPackageStartupMessages(library(tidyverse))
flakes_TL <- read_csv("Tham_Lod_Area_1_lithics.csv")
flakes_BR <- read_csv("Ban_Rai_Area_3_lithics.csv")
```

### Median % Dorsal Cortex
Many of the artifacts at Ban Rai have 0% dorsal cortex, though in the Marwick paper, this appears more extreme (Fig. 6). Tham Lod, has a median of 20% of dorsal cortex. 
```

```{r tidy-the-data}
# dorsal cortex and dorsal scars 
TL_dorsal <-
  flakes_TL %>% 
  select(DORSAL_COR, DORSAL_SCA, SITE, EXCAVATION)

BR_dorsal <-
  flakes_BR %>% 
  select(DORSAL_COR, DORSAL_SCA, SITE, EXCAVATION)

TL_BR_dorsal <- bind_rows(TL_dorsal, BR_dorsal)
```

```{r}
ggplot(TL_BR_dorsal, aes(SITE, DORSAL_COR)) +
  geom_boxplot()

```

### Mean Proportion of No Cortex
At Ban Rai, the mean proportion of no cortex found on artifacts was 20% higher than at Tham Lod. This result was slightly different than in the Marwick paper (Fig. 6), though the trend generally matched. 
```{r}

dorsal_cortex_proportion <- 
  TL_BR_dorsal %>% 
  group_by(SITE, EXCAVATION, DORSAL_COR) %>% 
  tally() %>% 
  mutate(DORSAL_COR = ifelse(DORSAL_COR == 0, "zero", "not zero")) %>% 
  group_by(SITE, EXCAVATION, DORSAL_COR) %>% 
  tally() %>% 
  filter(!is.na(DORSAL_COR)) %>% 
  spread(DORSAL_COR, n) %>% 
  mutate(dorsal_proportion = zero / (`not zero` + zero))

```

```{r}
ggplot(dorsal_cortex_proportion, aes(SITE, dorsal_proportion)) +
  geom_boxplot()
```

## Conclusion
This report generally came to the same conclusions that Marwick (2013) did in his paper, though the numbers are a little bit different even when using the same dataset. This suggests that only a subset of the data might have been used by Marwick in order to make the claims seem more robust, though the results are not drastically different.  Artifacts from Ban Rai seem to have been more intensively reduced, which Marwick suggests shows a logistical strategy, where as at Tham Lod, a residential strategy was probably practiced. This violated some of the predictions based on ecological models that Marwick made at the beginning of the paper, though this lack of fit between archaeological and ecological models is not unheard of and behavior may not only be for adaptive/functional reasons, instead influenced by cultural or other factors (Bird and O'Connell 2006).

## References cited

Bird, D., O’Connell, J., 2006. Behavioral ecology and archaeology. Journal of Archaeological Research 14, 143–188.

Chitkament, Thanon, Claire Gaillard, and Rasmi Shoocongdej. 2015. "Tham Lod rockshelter (Pang Mapha district, north-western Thailand): Evolution of the lithic assemblages during the late Pleistocene." Quaternary International: 1-11.

Marwick, B., 2008b. What attributes are important for the measurement of assemblage reduction intensity? results from an experimental stone artefact assemblage with relevance to the Hoabinhian of mainland Southeast Asia.Journal of Archaeological Science 35, 1189–1200.

Marwick, Ben. 2013. “Multiple Optima in Hoabinhian flaked stone artefact paleoeconomics and palaeoecology at two archaeological sites in Northwest Thailand.” Journal of Anthropological Archaeology 32: 553-564.

<!-- don't delete the line below, it will count the words in your report. You will need to do a one-time install of the wordcountaddin package first by running this code in your console: source("https://install-github.me/benmarwick/wordcountaddin") #  -->
Word count: `r wordcountaddin::word_count()`

### 2019-08-17 analysis/supplementary-materials/submitted-assigments/Ryan Robinson/Robinson_archy-483-replication-report-group-rollingstones.Rmd
resubmit after peer reviews

---
title: "Spring 2019 ARCHY 483 Replication Report"
author: "Ryan Robinson"
date: "`r Sys.Date()`"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE) # this ensures we can see your code in the output
```

## Introduction

The goal of this project was to replicate a portion of Marwick et al.'s study of the stone tool assemblage from Jerimalai (2016). Jerimalai is a site in East Timor with material culture dated to as early as 42,000 years ago. It is an important site for its geographical positioning, which played a role in the dispersal of humans throughout ISEA (Morwood et al., 2005). The authors analyzed the quantitative aspects of Jerimalai's assembalge and concluded that A) there is little change in lithic technology throughout Jerimalai's occupation; B) chert is the dominant lithic resource in use, instead of ISEA-typical pebbles; and C) the assemblage resembles the supposed Homo floresiensis assemblage at nearby Luang Bua.

Here, we focus on claim A from that paper. We obtained Marwick et al’s data and confirmed this claim through an R-based analysis of retouch and platform preparation (overhang removal) patterns over time.

## Methods

Marwick et al's paper claims that approximately 4-9% of flakes from the assemblage were retouched (Marwick et al., 2016). In our replication, we confirmed that, generating a plot that  shows the proportion of retouched pieces bouncing almost exclusively between 4% and 9%.

To do so, we calculated for the proportion of retouched pieces and compared that figure against spits, the stratigraphic labels that represent time, and displayed the results in a line plot.

The paper states that the number of pieces with signs of overhang removal (OHR) remained in a steady range for the entirety of Jerimalai's occupation (Marwick et al., 2016). The authors note that the presence of OHR typically signifies complex knapping methods. Their presence at Jerimalai stands at odds with the norm throughout other ISEA sites, which generally have simpler technology (O'Connor er al., 2011) Nonetheless, our analysis confirmed this claim as well.

Overhang removal is treated similarly to retouch in the original paper. Therefore, we used identical code to generate a new variable ("propoverhang") and display it on a line plot.

## Results

```{r read-in-the-data}
suppressPackageStartupMessages(library(tidyverse))
Jerimalai_Square_B_Data <- read_csv("Jerimalai_All_Artefacts_Square_B.csv")

```

```{r tidy-the-data}
Jerimalai_proprtch <- Jerimalai_Square_B_Data %>% 
  group_by(Spit, Rtch) %>% 
  tally() %>% 
  spread(Rtch, n) %>% 
  mutate(No = sum(No, `<NA>`, na.rm = TRUE)) %>% 
  select(- `<NA>`) %>% 
  mutate(proprtch = Yes/(Yes + No))
```

```{r}
Jerimalai_propoverhang <- Jerimalai_Square_B_Data %>% 
  group_by(Spit, Overhang) %>% 
  tally() %>% 
  spread(Overhang, n) %>% 
  mutate(No = sum(No, `<NA>`, na.rm = TRUE)) %>% 
  select(- `<NA>`) %>% 
  mutate(propoverhang = Yes/(Yes + No))
```

```{r plot-the-data}
ggplot(Jerimalai_proprtch, 
       aes(x = Spit, 
           y = proprtch)) + 
  geom_line() +
  ylim(0, 1)
```

This plot graphs the changes in retouch proportions over time. We can make two observations: first, that the proportion of retouched flakes was always low; and second, that it always remained firmly within its narrow margins. We also see some minor fluctuations in the form of prolonged periods of lower or higher retouch activity, but nothing that breaks the overall pattern.

```{r}
ggplot(Jerimalai_propoverhang, 
       aes(x = Spit, 
           y = propoverhang)) + 
  geom_line() +
  ylim(0, 1)
```

This plot displays variations in OHR practices over Jerimalai's occupation. Like the first plot, we see a relatively stable line, indicating a consistent presence of OHR throughout Jerimalai's past. However, there seems to have been some meaningful changes here. The plot reveals a steady increase in OHR that suddenly drops off around the 12th split. This change does not coincide with anything in the retouch plot, but nonetheless suggests an interesting technological shift.

## Conclusion

We tested the authors' claims regarding the consistency of the lithic technology at Jerimalai over the course of its human occupation, which began 42,000 years ago. We found that their observations are reliable, though it appears that an investigation into the fluctuation of OHR practice may reveal some qualitative information about the site's history. This might be worth exploring in future studies.

## References cited

source("https://install-github.me/benmarwick/wordcountaddin")
<!-- don't delete the line below, it will count the words in your report. You will need to do a one-time install of the wordcountaddin package first by running this code in your console: source("https://install-github.me/benmarwick/wordcountaddin") #  -->
Word count: `r wordcountaddin::word_count()`

### 2019-08-17 analysis/paper/plot-feedback-survey.R

@@ -69,7 +69,7 @@ plot_grid(plot_l,
           rel_heights = c(4, 1))
 
 ggsave(plot = feedback_plots,
-       here::here('analysis/figures/feedback_likert_yn_plot.png'),
+       here::here('analysis/figures/feedback_likert_yn_plot.jpg'),
                   width = 5.75,
        dpi = 300)
 
@@ -89,7 +89,7 @@ feedback_likert_out$results %>%
   theme(axis.text=element_text(size=6))
 
 ggsave(plot = feedback_likert_out_plot,
-       here::here('analysis/figures/feedback_likert_corr.png'),
+       here::here('analysis/figures/feedback_likert_corr.jpg'),
        width = 5.75,
        h = 5.75,
        dpi = 300)

### 2019-08-17 analysis/paper/plot-rubric-scores.R

@@ -74,9 +74,15 @@ scores %>%
   theme_minimal(base_size = 8) +
   coord_flip()
 
-ggsave(plot = rubric_data_plot,
-       here::here('analysis/figures/rubric_score_distribution.png'),
-       width = 5.75)
+ggplot2::ggsave(plot = rubric_data_plot,
+       here::here('analysis/figures/rubric_score_distribution.jpg'),
+       width = 5.75,
+       dpi = 300)
 
+# details on figure size
+# electronically as high-resolution TIFF, EPS, or JPG files for best print reproduction.
+# https://documents.saa.org/container/docs/default-source/doc-publications/style-guide/saa-style-guide_updated-july-2018c5062f7e55154959ab57564384bda7de.pdf?sfvrsn=8247640e_6
+# A minimum of 300 dpi
+# The maximum dimensions of a published figure are 5.75 inches (ca. 15 cm) by 8 inches (20.3 cm).
 
 

### 2019-08-17 README.Rmd
update readme to show supplementary materials

--- 2019-08-16 README.Rmd
@@
 - [:file_folder: figures](/analysis/figures): Plots and other illustrations
+- [:file_folder: supplementary-materials](/analysis/supplementary-materials): Supplementary materials including the assignment instructions that we used with the students, and two completed assignments submitted by students in this class.
 
